---
title: "R Notebook"
output: html_notebook
---

```{r}
library(plyr)
library(dplyr)
library(permute)
library(raster)
library(smoothie)
library(tidyr)
library(data.table)
library(datatrace)
library(DT)

# Testing
library(lmerTest)
library(BayesFactor)
options(BFprogress = FALSE)

# Plotting
library(ggplot2)
library(cowplot)
library(plotly)
gtheme = theme_minimal() + theme_cowplot() +
  theme(text = element_text(size=10), axis.text = element_text(size=8))

summarise = dplyr::summarise
summarize = dplyr::summarize
select = dplyr::select

source('distances.R')
source('fixed_effects.R')
source('locations.R')
source('place_field_utils.R')
source('utils.R')
source('plotting_params.R')
```

The code assumes data frames with place fields information are loaded in the environment (created by Fig1-calculate_place_cells.R)

Prepare data frames
```{r}
mouse.meta.df = read.mouse.meta(rootdirs)
trials.meta.df = read.trials.meta(rootdirs)

run.trials.si$date = char2date(run.trials.si$date)
beforetest.trials.si$date = char2date(beforetest.trials.si$date)
run.trials.si = run.trials.si %>%
  left_join(mouse.meta.df, by='animal') %>%
  left_join(trials.meta.df, by=c('date', 'animal'))
```



```{r calculate early vs late correlations}
cell.cor = function(animal_name, day, cell_name) {
  early.pf = create.partial.df(early.fields, early.occupancies, animal_name, day, cell_name, 'Early')
  late.pf = create.partial.df(late.fields, late.occupancies, animal_name, day, cell_name, 'Late')
  if (nrow(late.pf) == 0 || nrow(early.pf) == 0) {
    return(0)
  }
  x = field.cor(early.pf, late.pf, nbins, make.cor.plot=FALSE)

  return(x$cor)
}

run.trials.si = run.trials.si %>%
  dplyr::rowwise() %>%
  dplyr::mutate(early.late.cor = cell.cor(animal, format(date), cell_id))
```

```{r classify place cells}
mi.thresh = -1.0
field.size.thresh.50 = 100
field.size.thresh.25 = 100
field.peak.thresh = 0
field.cor.min = 0.0

# Classification of place cells based on day SI
run.trials.pc = run.trials.si

place.cell.db = run.trials.si %>%
  dplyr::select(date, day_desc, exp, animal, cell_id, implant, 
                spatial.information, si.shuffle.mean, 
                mutual.info, mutual.info.bias,
                sparsity, field.size.50, field.size.25, 
                field.max, field.mean, trace.mean,
                early.late.cor, signif.mi, signif.si) %>%
  ungroup()


pc.test.df = beforetest.trials.si %>%
  left_join(mouse.meta.df, by='animal') %>%
  left_join(trials.meta.df, by=c('date', 'animal')) %>%
  dplyr::mutate(beforetest_ordinal=location_set-1) %>%
  dplyr::select(-location_set)

beforetest.cell.db = pc.test.df %>%
  dplyr::select(date, day_desc, exp, animal, cell_id, implant, 
                spatial.information, si.shuffle.mean, mutual.info, mutual.info.bias,
                sparsity, field.size.50, field.size.25,
                signif.mi, signif.si)
```

Percent of place cells out of all cells
```{r place_cell_summary}
place.cell.db %>%
  group_by(implant, animal, exp) %>%
  dplyr::summarise(si.signif.pct=sum(signif.si)/n() * 100) %>%
  group_by(implant, exp) %>%
  dplyr::summarise(mean(si.signif.pct),
                   sem(si.signif.pct))
```


## Comparison of dCA1 and vCA1 place fields: pct of place cells, field size, early late corr
```{r}
compared.pcs.df = place.cell.db %>%
  filter(exp=='habituation') %>% 
  mutate(exp_title='habituation') %>%
  left_join(trials.meta.df) %>%
  left_join(mouse.meta.df) %>%
  mutate(aday = paste(animal, format(date), sep='_'),
         spatial.info.corrected = spatial.information - si.shuffle.mean)
compared.pcs.df$aday = as.factor(compared.pcs.df$aday) %>% as.integer() %>% as.factor()
single.day.pcs.df = filter(compared.pcs.df, day_desc=='habituation day#3', signif.si)

plot.pc.stat = function(metric, facet.exp_title=FALSE) {
  metric = enexpr(metric)
  xvar = quo(implant)
  if (facet.exp_title) {
    xvar = quo(exp_title)
  }
  g = single.day.pcs.df %>%
    ggplot(aes(x=!!xvar, y=!!metric)) +
    geom_violin(fill=single.colour, color=single.colour)+ 
    geom_violin(fill='transparent', colour='white', draw_quantiles=0.5, size=0.4) +
    geom_jitter(shape=16, width=0.4, height=0, size=0.1, alpha=0.15, color='#333333')+
    gtheme +
    xlab('') +
    theme(axis.title.x = element_blank(),
          legend.position = 'top')
  if (facet.exp_title) {
    g = g + facet_grid(. ~ implant)
  }
  g
}

summary.compared.pcs.df = compared.pcs.df %>%
  group_by(implant, animal, day_desc, exp_title) %>%
  dplyr::summarise(pc.pct = mean(signif.si) * 100)

g.place.cell.count = summary.compared.pcs.df %>%
  ggplot(aes(x=implant, y=pc.pct, colour=implant)) +
  stat_summary(fun.data='mean_cl_boot', geom='crossbar') +
  geom_jitter(shape=1, width=0.2, height=0, size=0.5) +
  scale_color_manual(values=main.two.colours) +
  gtheme +
  ylab('Place cells (%)') + xlab('') + ylim(c(0,100)) +
  theme(axis.title.x = element_blank(),
        legend.position = 'none')
 
plot_grid(
  g.place.cell.count,
  plot.pc.stat(field.size.50 / nbins / nbins * 100) +
    ylab('% of maze'),
  plot.pc.stat(spatial.information-si.shuffle.mean) + ylab('bits'),
  plot.pc.stat(early.late.cor) + ylab('correlation'),
  nrow = 1, rel_widths = c(0.95,1,1,1))

figure.ggsave('Figure_1DEGH.pdf', width=12.5, height=2.9)
```


```{r}
print('Field size signif larger in vCA1')
field.size.model = lmerTest::lmer(log(field.size.50 ) ~ implant + (1 | aday), 
                                  data=single.day.pcs.df, REML=TRUE)
summary(field.size.model)
anova(field.size.model, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(field.size.model, 
                       single.day.pcs.df$animal, 
                       single.day.pcs.df$implant)
create.summary(mutate(single.day.pcs.df, field.size=field.size.50/nbins/nbins*100), 
               field.size, implant)

models = create.bayes.lm.pair(mutate(single.day.pcs.df, val=log(field.size.50)))
models$full/models$null
calc.pair.95CI(models$full, function(x) {exp(x) * 100})
```

```{r}
print('Percent of place cells not different')
pc.count.model = lmerTest::lmer(pc.pct ~ implant + (1 | animal), data=summary.compared.pcs.df, REML=TRUE)
summary(pc.count.model)
anova(pc.count.model, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(pc.count.model, 
                       summary.compared.pcs.df$animal, 
                       summary.compared.pcs.df$implant)
group_by(summary.compared.pcs.df, implant) %>%
  dplyr::summarise(mean(pc.pct), sem(pc.pct))
dplyr::summarise(ungroup(summary.compared.pcs.df), mean(pc.pct), sem(pc.pct))

models = create.bayes.lm.pair(summary.compared.pcs.df,
                              formula.full = pc.pct ~ 1 + implant + animal,
                              formula.null = pc.pct ~ 1 + animal,
                              whichRandom = 'animal')
models$full/models$null
calc.pair.95CI(models$full, show.percent.change = FALSE)
```

```{r}
print('Spatial information not statistically different')
spatial.info.model = lmerTest::lmer(log(0.2 + spatial.info.corrected) ~ implant + (1 | aday), 
                                    data=single.day.pcs.df, REML=TRUE)
summary(spatial.info.model)
anova(spatial.info.model, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(spatial.info.model, 
                       single.day.pcs.df$animal, 
                       single.day.pcs.df$implant)

models = create.bayes.lm.pair(mutate(single.day.pcs.df, val=log(0.2 + spatial.info.corrected)))
models$full/models$null
calc.pair.95CI(models$full, function(x) {(exp(x) - 0.2)})
create.summary(single.day.pcs.df, spatial.info.corrected, implant)

print('Day-stability not statistically different')
create.summary(single.day.pcs.df, early.late.cor)
create.summary(single.day.pcs.df, early.late.cor, implant)
early.late.cors.model = lmerTest::lmer(early.late.cor ~ implant + (1 | aday), 
                                       data=subset(single.day.pcs.df, exp_title=='habituation'), 
                                       REML=TRUE)
summary(early.late.cors.model)
anova(early.late.cors.model, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(early.late.cors.model, 
                       subset(single.day.pcs.df, !is.na(early.late.cor) & exp_title=='habituation')$animal, 
                       subset(single.day.pcs.df, !is.na(early.late.cor) & exp_title=='habituation')$implant)
models = create.bayes.lm.pair(filter(single.day.pcs.df, !is.na(early.late.cor)) %>% mutate(val=early.late.cor))
models$full/models$null
calc.pair.95CI(models$full, show.percent.change = FALSE)
```
    

# Pct of place cells within goal
Load reward locations
```{r}
all.locations.df = map_dfr(rootdirs, read_locations)
rewards.df =  all.locations.df %>%
  filter(!is_test) %>%
  left_join(mouse.meta.df, by='animal') %>%
  left_join(trials.meta.df, by=c('date', 'animal', 'location_set'))

locations.df = rewards.df %>%
  dplyr::select(date, animal, location_set) %>%
  dplyr::distinct()

locations.df = data.table(locations.df)
setkey(locations.df, date, animal)

test.rewards.df = all.locations.df %>%
  filter(is_test) %>%
  left_join(mouse.meta.df, by='animal') %>%
  left_join(dplyr::select(trials.meta.df, -location_set), by=c('date', 'animal'))
```


# Place cells at previous reward location
```{r}
prev.locations.df = all.locations.df %>%
  filter(!is_test) %>%
  add_prev_locations(prev.loc.set.diff=1) %>%
  add_prev_locations(prev.loc.set.diff=2) %>%
  add_prev_locations(prev.loc.set.diff=3) %>%
  filter()
```

```{r}
fst.moved.location.df = all.locations.df %>%
  filter(!is_test) %>%
  add_prev_locations(prev.loc.set.diff=1) %>%
  filter(!current_loc, prev_loc_set==1) %>%
  ungroup() %>%
  dplyr::select(-date) %>%
  dplyr::distinct()
```


For each place field calculate the count of its peaks, and how many of them are in the reward zone or previous reward zone
```{r warning=FALSE}
trial.days.df = trials.meta.df %>%
  dplyr::select(date, animal, exp) %>%
  filter(animal != 'missing') %>%
  dplyr::distinct()

create.peaks.df.at.locs = function(fields, locs.df, trial.days, max.rew.dist.thr=goal.cell.max.dist, cell.db=place.cell.db) {
  res = map2_dfr(trial.days$date,
                 trial.days$animal,
                 ~ {
                    .x = format(.x)
                    .y = as.character(.y)
                     if ((.y %in% names(fields)) & (.x %in% names(fields[[.y]]))) {
                       calc.field.peaks.info(.x, .y, 
                                             fields[[.y]][[.x]], 
                                             rew.df=filter.rews.df(locs.df, .x, .y),
                                             max.rew.dist.thr)
                     } else {
                       warning('Not found animal=', .y, ' on day=', .x)
                       return(data.frame())
                     }
                   })
  res$date = char2date(res$date)
  res %>%
    left_join(trials.meta.df, by=c('animal', 'date')) %>%
    left_join(cell.db, by=c('animal', 'date', 'cell_id', 'day_desc', 'exp'))
}

trial.peaks.at.rew = create.peaks.df.at.locs(run.fields, prev.locations.df, trial.days.df)
trial.peaks.at.fst.moved = create.peaks.df.at.locs(run.fields, fst.moved.location.df, trial.days.df)
trial.peaks.at.current.rew = create.peaks.df.at.locs(run.fields, prev.locations.df[current_loc==TRUE,], trial.days.df)

beforetest.peaks.at.rew = create.peaks.df.at.locs(beforetest.fields, prev.locations.df, trial.days.df, 
                                                  cell.db=beforetest.cell.db)
beforetest.peaks.fst.moved = create.peaks.df.at.locs(beforetest.fields, fst.moved.location.df, trial.days.df,
                                                     cell.db=beforetest.cell.db)
beforetest.rewards.df$current_loc = FALSE
beforetest.peaks.at.current.rew = create.peaks.df.at.locs(beforetest.fields, beforetest.rewards.df, trial.days.df,
                                                          cell.db=beforetest.cell.db)

habituation.peaks.at.fst.moved = filter(trial.peaks.at.fst.moved, exp=='habituation')
```

Peaks in place fields from habituation with regards to first reward locations
```{r warning=FALSE}
habittest.daypair = filter(trials.meta.df, exp == 'habituation') %>%
  left_join(dplyr::select(beforetest.rewards.df, date, animal, location_set), 
            by=c('animal'), suffix=c('.habitday', '.testday'))
habit.fields.at.test.rews = map_dfr(1:nrow(habittest.daypair), ~ {
  animal_name = as.character(habittest.daypair$animal[.x])
  activity_date = as.Date(habittest.daypair$date.habitday[.x])
  test_date = as.Date(habittest.daypair$date.testday[.x])
  rew.df = beforetest.rewards.df[animal==animal_name & date == test_date,]
  calc.field.peaks.info(activity_date,
                        animal_name,
                        run.fields[[animal_name]][[format(activity_date)]], 
                        rew.df=rew.df,
                        max.rew.dist.thr=goal.cell.max.dist) %>%
    dplyr::mutate(date.active = activity_date,
                  day_desc.active = habittest.daypair$day_desc[.x],
                  date.reward = test_date)
})
habit.fields.at.test.rews = habit.fields.at.test.rews %>%
  dplyr::select(-date) %>%
  left_join(trials.meta.df, by=c('animal'='animal', 'date.reward'='date'), suffix=c('', '.reward')) %>%
  dplyr::select(-day_ordinal, -exp, -location_set, -current.rew.peaks.count) %>%
  dplyr::rename(day_desc.reward = day_desc) %>%
  left_join(place.cell.db, by=c('animal'='animal', 'date.active'='date', 'cell_id'='cell_id', 'day_desc.active'='day_desc'))
```

## Summary on multiple fields per cell

Fields per cell in dca1 and vCA1
```{r}
npeaks.summary = bind_rows(
    filter(trial.peaks.at.fst.moved, exp == 'habituation'),
    beforetest.peaks.fst.moved) %>% 
  filter(signif.si, npeaks > 0) %>%
  #filter(day_desc == 'habituation day#3') %>% 
  group_by(implant, exp, animal, day_desc) %>%
  dplyr::summarise(create.hist.tibble(npeaks, hist.breaks=seq(0.5,6,1)), ncells=n()) %>%
  filter(ncells >= 5) # Only include samples with >= 5 cells

# Fraction of multifields
npeaks.summary %>%
  ungroup() %>%
  filter(mid == 1) %>%
  group_by(implant) %>%
  dplyr::summarise(mean.multi = mean(100-pct.count), sem.multi = sem(100-pct.count))

plotted.npeaks.summary = npeaks.summary %>%
  group_by(implant, exp, mid) %>%
  dplyr::summarise(pct.mean = mean(pct.count), pct.sem = sem(pct.count)) 

plotted.npeaks.summary %>% 
  filter(exp=='habituation') %>%
  ggplot(aes(x=mid, color=implant)) +
  geom_errorbar(aes(ymin=pct.mean - pct.sem, ymax=pct.mean + pct.sem), width=0.3) +
  geom_step(aes(x=mid-0.5, y=pct.mean)) +
  scale_color_manual(values=main.two.colours) +
  xlab('# fields') + ylab('Place cells (%)') +
  xlim(c(0.5,4.5)) + 
  gtheme +
  labs(color='')

figure.ggsave('Figure_1G.pdf', width=6.1, height=3.6)
```

```{r}
npeaks.habituation = filter(trial.peaks.at.fst.moved, exp == 'habituation') %>%
  filter(signif.si, npeaks>0) %>%
  group_by(implant, exp, animal, day_desc) %>%
  dplyr::summarise(mean.peaks = mean(npeaks))

npeaks.habituation %>%
  create.summary(mean.peaks, implant)

lmer.test.print(npeaks.habituation, 
                var = mean.peaks,
                fixed.effects = implant,
                randef.str = '(1 | animal)',
                diagnostics.groupvar = implant)
models = create.bayes.lm.pair(npeaks.habituation,
                              formula.full = mean.peaks ~ 1 + implant + animal,
                              formula.null = mean.peaks ~ 1 + animal,
                              whichRandom = 'animal')
models$full / models$null
calc.pair.95CI(models$full)
```


# Distribution of ditances to the rewards
```{r}
compared.habit.fields.at.test.rews = habit.fields.at.test.rews %>%
  filter(signif.si, exp == 'habituation', day_desc.active == 'habituation day#3') %>%
  dplyr::select(-ends_with('.active')) %>%
  dplyr::rename(date=date.reward,
                day_desc=day_desc.reward)

plot.densities = function(df, xvar.expr, fill.var, ..., include.means=FALSE) {
  xvar.expr = enexpr(xvar.expr)
  fill.var = enquo(fill.var)
  group.vars = c(fill.var, enquos(...))
  
  df = unite(df, 'groups.concat', map_chr(group.vars, as_label), remove = FALSE) 
  xvar.mean.summary = group_by(df, implant, groups.concat, !!!group.vars) %>%
    dplyr::summarise(xvar.mean=mean(!!xvar.expr, na.rm=TRUE),
                     .groups='drop')
  
  g = df %>%
    ggplot(aes(x=!!xvar.expr, group=groups.concat)) +
    geom_density(aes(fill=!!fill.var), alpha=0.3, adjust=1, color='#333333') +
    scale_fill_manual(values=c('#999999', '#0098ff')) +
    scale_color_manual(values=c('#999999', '#0098ff')) +
    gtheme +
    ylab('Density')
  if (include.means) {
    g = g +
      geom_vline(data=xvar.mean.summary,
                 mapping=aes(xintercept=xvar.mean, color=!!fill.var),
                 linetype='longdash')
  }
  g
}

bind_rows(
  mutate(compared.habit.fields.at.test.rews, group.name='1_habituation'),
  filter(beforetest.peaks.at.current.rew, signif.si) %>% mutate(group.name='2_test')
) %>%
  plot.densities(min.rew.dist * perc2dist, group.name) +
  geom_vline(xintercept = goal.cell.max.dist, linetype='dotted') +
  xlim(c(0,100)) +
  facet_grid(. ~ implant) +
  coord_flip() +
  xlab('Distance (cm)')
figure.ggsave('Figure_2FH_Left.pdf', height=6, width=8)
```


## Multifield distance to the closest reward
```{r}
habit.summary.fields.pct.df = summarize.rew.pc.pct(
  filter(compared.habit.fields.at.test.rews),
  dist.var=min.rew.dist, 
  dist.threshold=goal.cell.max.dist) %>% dplyr::ungroup()

beforetest.summary.fields.pct.df = summarize.rew.pc.pct(
  filter(beforetest.peaks.at.current.rew, signif.si),
  dist.var=min.rew.dist, 
  dist.threshold=goal.cell.max.dist)

merged.summary.df = bind_rows(
  habit.summary.fields.pct.df %>% mutate(exp='habituation'),
  beforetest.summary.fields.pct.df %>% mutate(exp='test')) %>%
  mutate(animal_beforetest_day = paste(animal, day_desc, sep='_'))
  #filter(animal_beforetest_day %in% kept.testtrials$animal_beforetest_day)
merged.summary.df$exp = as.factor(merged.summary.df$exp)
merged.summary.df$aday = as.factor(merged.summary.df$animal_beforetest_day) %>% as.integer %>% as.factor

dca1.rew.pc.pct = subset(merged.summary.df, implant == 'dCA1')
vca1.rew.pc.pct = subset(merged.summary.df, implant == 'vCA1')

print('Fraction of dCA1 place cells at reward increased')
fem.model = lmerTest::lmer(pct.reward ~ exp*implant + (1 + exp + day_desc | animal), 
                           data=merged.summary.df, REML = TRUE)
plot.model.diagnostics(fem.model, merged.summary.df$implant, merged.summary.df$exp)
anova(fem.model, refit=FALSE, ddf='Satterthwaite')
pairwise.post.hoc(fem.model, factor.interaction=c('exp:implant'))
create.summary(merged.summary.df, pct.reward, implant, exp)

models = create.bayes.lm.pair(dca1.rew.pc.pct,
                     formula.full = pct.reward ~ 1 + exp + aday + animal,
                     formula.null = pct.reward ~ 1 + aday + animal,
                     whichRandom = c('aday', 'animal'))
models$full / models$null
calc.pair.95CI(models$full, pair.vars = c('exp-habituation', 'exp-test'))

models = create.bayes.lm.pair(vca1.rew.pc.pct,
                     formula.full = pct.reward ~ 1 + exp + aday + animal,
                     formula.null = pct.reward ~ 1 + aday + animal,
                     whichRandom = c('aday', 'animal'))
models$full / models$null
calc.pair.95CI(models$full, pair.vars = c('exp-habituation', 'exp-test'))

animal.merged.summary.df = merged.summary.df %>%
  group_by(implant, animal, exp) %>%
  dplyr::summarise(pct.reward.mean = mean(pct.reward),
                   n=n())

merged.summary.df %>%
  ggplot(aes(x=exp, y=pct.reward, group=animal_beforetest_day)) +
  geom_line(size=0.25, color='#888888') +
  geom_line(data=animal.merged.summary.df, 
            mapping=aes(y=pct.reward.mean, group=animal),
            size=0.5, color='#333333') +
  facet_grid(. ~ implant, scales = 'free') +
  xlab('') +
  gtheme +
  ylab('Place cells at reward (%)') +
  ggtitle('Fraction of place cells at reward increased at test trial')


figure.ggsave('Figure_2H.pdf', height=5, width=4.9)
```
```{r}
print("Saving processed place field stats")
save.image(file="data/place_field_stats.RData")
```

