---
title: "Cheeseboard learning analysis"
output:
  html_document:
    df_print: paged
---

Before running the notebook run trial_stats.R.

```{r imports, include=FALSE}
library(dplyr)
library(ggplot2)
library(cowplot)
library(readr)
library(tidyr)
library(purrr)

library(datatrace)

source('crossings.R')
source('distances.R')
source('locations.R')
source('tracking_files.R')
source('tracking_info.R')
source('traces_input.R')
source('plotting_params.R')
```

```{r}
dir = '/mnt/DATA/Prez/cheeseboard'
hab_dirs = map_chr(tracking_rootdirs, ~ paste(.x, 'habituation', sep='/'))
gen_imgs_dir = '~/tmp/cheeseboard/learning/'

df = read_csv(paste0(dir, '/trial_stats.csv'))
locations.df = map_dfr(rootdirs, read_locations)
trials.meta.df = read.trials.meta(rootdirs)
mouse.meta.df = read.mouse.meta(rootdirs)

behav_cam_frame_rate = 24
cheeseboard.len.cm = 120
```


```{r}
df = dplyr::mutate(df, total_trial_n = 8*(learning_day1 - 1) + trial_n)

notest.df = filter(df, exp_title == 'trial')
d = notest.df 
d$learning_day1 = as.factor(d$learning_day1)
```

Distance run in learning trials shown over time
```{r}
alltrial.mean.dist = d2 %>% 
  filter(time_finished > 0 & time_finished <= 180) %>%
  mutate(dist_m = total_dist / cheeseboard.len.cm) %>%
  group_by(total_trial_n) %>%
  dplyr::summarise(mean.total_dist = mean(dist_m),
                   sem.total_dist = sem(dist_m))
ggplot(alltrial.mean.dist, aes(x=as.integer(total_trial_n))) +
  geom_errorbar(aes(ymin=mean.total_dist-sem.total_dist,
                  ymax=mean.total_dist+sem.total_dist,
                  group=1), color='#333333') +
  geom_vline(xintercept=40.5, linetype="dashed", color = "#444444") +
  geom_vline(xintercept=56.5, linetype="dashed", color = "#444444") +
  geom_vline(xintercept=72.5, linetype="dashed", color = "#444444") +
  scale_x_continuous(limits=c(0,72.5), breaks=seq(1, 72, 8)) +
  xlab('Trial') +
  ylab('Distance travelled (m)') +
  gtheme

figure.ggsave('Figure_2B-learning_trials_distance.pdf', width=6.5, height=3.6)
```

# Number of crossings in trial tests
```{r}
test.trial.df = df %>%
  mutate(learning_day1_f = as.factor(learning_day1),
         crossings_0_60s=crossings_0_30s+crossings_30_60s,
         crossings_0_120s=crossings_0_60s+crossings_60_90s+crossings_90_120s,
         crossings_per_min=crossings_n/(total_frames/behav_cam_frame_rate) * 60,
         dist_0_60s = dist_0_30s + dist_30_60s,
         dist_0_120s = dist_0_60s + dist_60_90s + dist_90_120s,
         norm_crossings_30s=crossings_0_30s / (dist_0_30s / cheeseboard.len.cm),
         norm_crossings_60s=crossings_0_60s / (dist_0_60s / cheeseboard.len.cm),
         norm_crossings_120s=crossings_0_120s / (dist_0_120s / cheeseboard.len.cm)) %>%
  filter(exp_title == 'beforetest') 
```

Calculate number of crossings during habituation for each location set
```{r, warning=FALSE}
hab.files = map_dfr(hab_dirs, get_tracking_files) %>%
  filter(exp_title != 'homecage')
animal.locations = locations.df %>%
  dplyr::mutate(rowxcol=paste0(as.character(Well_row), 'x', as.character(Well_col))) %>%
  filter(Valence == 'Positive') %>%
  filter(is_test == FALSE) %>%
  group_by(animal, rowxcol, location_set) %>%
  dplyr::select(animal, rowxcol, Well_row, Well_col, trans_x, trans_y, location_set) %>%
  dplyr::distinct()

hab_loc = full_join(hab.files, animal.locations, by=c("animal")) %>%
  filter(!is.na(filepath))
hab_loc$crossings = rep(0, nrow(hab_loc))
hab_loc$total_dist = rep(0, nrow(hab_loc))
hab_loc$total_frames = rep(0, nrow(hab_loc))
for (i in 1:nrow(hab_loc)) {
  tracking.df = read_csv(hab_loc$filepath[i], col_types = cols())
  tracking.df.filtered = filter(tracking.df, trans_x > 0, trans_y > 0) %>%
    arrange(timestamp)
  crossings = crossings4positions(
                      tracking.df.filtered$smooth_trans_x, tracking.df.filtered$smooth_trans_y, 
                      hab_loc$trans_x[i], hab_loc$trans_y[i], rew_zone_radius)
  hab_loc$crossings[i] = crossings
  frame_60s = behav_cam_frame_rate * 60
  frame_120s = behav_cam_frame_rate * 120
  hab_loc$crossings_0_60s[i] = crossings4positions(
                      tracking.df.filtered$smooth_trans_x[1:frame_60s], tracking.df.filtered$smooth_trans_y[1:frame_60s], 
                      hab_loc$trans_x[i], hab_loc$trans_y[i], rew_zone_radius)
  hab_loc$crossings_0_120s[i] = crossings4positions(
                      tracking.df.filtered$smooth_trans_x[1:frame_120s], tracking.df.filtered$smooth_trans_y[1:frame_120s], 
                      hab_loc$trans_x[i], hab_loc$trans_y[i], rew_zone_radius)
  distances = vec_dist(tracking.df.filtered$smooth_trans_x, tracking.df.filtered$smooth_trans_y)
  hab_loc$dist_0_60s[i] = sum(distances[1:frame_60s])
  hab_loc$dist_0_120s[i] = sum(distances[1:frame_120s])
  hab_loc$total_dist[i] = sum(distances)
  hab_loc$total_frames[i] = last(tracking.df.filtered$frame) - first(tracking.df.filtered$frame)
}

```
Average across different trials
```{r}
hab.loc.set.crossings = group_by(hab_loc, filepath, filename, date, animal, trial, exp_title, location_set) %>%
  dplyr::summarize(crossings = sum(crossings),
                   crossings_0_60s = sum(crossings_0_60s),
                   crossings_0_120s = sum(crossings_0_120s),
                   dist_0_60s = mean(dist_0_60s),
                   dist_0_120s = mean(dist_0_120s),
                   total_dist = mean(total_dist),
                   total_frames = mean(total_frames)) %>%
  dplyr::mutate(norm_crossings = crossings / (total_dist  / cheeseboard.len.cm))

mhab_loc = hab.loc.set.crossings %>%
  group_by(animal, location_set) %>%
  dplyr::summarise(mnorm_crossings = mean(norm_crossings),
                   mcrossings_0_60s = mean(crossings_0_60s),
                   mcrossings_0_120s = mean(crossings_0_120s)) %>%
  dplyr::rename(norm_crossings=mnorm_crossings, 
                crossings_0_60s=mcrossings_0_60s, 
                crossings_0_120s=mcrossings_0_120s) %>%
  dplyr::mutate(type="habituation")
```

Compare crossings in probe tests vs habituation
```{r}
mhab_loc.filtered = mhab_loc %>% filter(animal %in% unique(test.trial.df$animal))
mhab_loc.perdate = test.trial.df %>%
  dplyr::select(animal, location_set, date) %>%
  left_join(mhab_loc.filtered, by=c('animal', 'location_set'))

mouse.meta.df = read.mouse.meta(rootdirs)
trials.meta.df$date = char2date(trials.meta.df$date)
test.trial.df.joined = test.trial.df %>%
  dplyr::select(animal, location_set, date, norm_crossings_120s, crossings_0_60s, crossings_0_120s) %>%
  dplyr::rename(norm_crossings = norm_crossings_120s) %>%
  dplyr::mutate(type="test")  %>%
  bind_rows(mhab_loc.perdate) %>%
  left_join(dplyr::select(trials.meta.df, -location_set), by=c('animal', 'date')) %>%
  left_join(mouse.meta.df, by=c('animal'))

test.trial.df.joined$type = as.factor(test.trial.df.joined$type)
test.trial.df.joined$location_set = as.factor(test.trial.df.joined$location_set)
```

```{r}
animal.test.trial.df.joined = test.trial.df.joined %>%
  group_by(implant, animal, type) %>%
  dplyr::summarise(norm_crossings.mean = mean(norm_crossings, na.rm=TRUE),
                   n=n())

test.trial.df.joined %>%
  mutate(animal_day_desc = paste(animal, day_desc, sep='_')) %>%
  ggplot(aes(x=type, y=norm_crossings, group=animal_day_desc)) +
  geom_line(size=0.25, color='#888888') +
  geom_line(data=animal.test.trial.df.joined, 
            mapping=aes(y=norm_crossings.mean, group=animal),
            size=0.5, color='#333333') +  
  facet_grid(. ~ implant) +
  ylab('Crossings per m') +
  gtheme

figure.ggsave('Figure_2D-learning_performance.pdf',
       width=4.6, height=3.5)
```
Statistical tests
```{r}
source('fixed_effects.R')
m = lmerTest::lmer(norm_crossings ~ type + implant + (1 + day_desc | animal),
                   test.trial.df.joined,
                   REML = FALSE)
summary(m)
anova(m, refit=FALSE, ddf='Satterthwaite')
plot.model.diagnostics(m, test.trial.df.joined$animal, test.trial.df.joined$implant)

dplyr::group_by(test.trial.df.joined, type) %>%
  dplyr::summarise(mean(norm_crossings), sem(norm_crossings))

```


```{r}
test.trial.df.joined = mutate(test.trial.df.joined, 
                              aday=paste(animal, day_desc, sep='_'))
test.trial.df.joined$aday = as.factor(test.trial.df.joined$aday) %>% as.integer() %>% as.factor()
bf.models = create.bayes.lm.pair(test.trial.df.joined,
                                 formula.full = norm_crossings ~ type + implant + aday,
                                 formula.null = norm_crossings ~ type + aday,
                                 whichRandom = c('aday'))
bf.models$full / bf.models$null
print('CI for difference between implants')
calc.pair.95CI(bf.models$full)

bf.models = create.bayes.lm.pair(test.trial.df.joined,
                                 formula.full = norm_crossings ~ type + aday,
                                 formula.null = norm_crossings ~ aday,
                                 whichRandom = c('aday'))
bf.models$full / bf.models$null
print('CI for difference between foraging and test')
calc.pair.95CI(bf.models$full, pair.vars = c('type-habituation', 'type-test'))
```


# Example of paths during beforetest 120s

Prepare traces
```{r}
source('utils.R')
root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2020-01/'
animal_name = 'K-BR'
exp_title='learning'
day = '2020-02-06' # learning 2 day1
caimg_result_dir = find.caimg.dir(caimg_result_dirs, animal_name, day)
beforetest.traces = read.data.trace(caimg_result_dir, 'beforetest')
```

```{r}
behav.traces.fragment = filter(beforetest.traces, 
                               cell_id == beforetest.traces$cell_id[1]) %>%
  filter(timestamp <= 120 * 1000) %>%
  arrange(timestamp)
behav.traces.fragment$row_id = 1:nrow(behav.traces.fragment)
behav.traces.fragment %>%
  ggplot() +
  geom_path(aes(x=x, y=100-y), size=0.5, colour='#666666') +
  geom_rewards.current(filter(test.rewards.df, exp_title=='beforetest'), 
               beforetest.traces$animal[1], beforetest.traces$date[1], nbins = 100, 
               rew.size=4, stroke.size=1) +
  geom_reward_zone(filter(test.rewards.df, exp_title=='beforetest'), 
               beforetest.traces$animal[1], beforetest.traces$date[1]) +
  geom_maze_contour(100) +
  scale_color_continuous(low='#b8e2ff', high='#222222') +
  theme_void() +
  theme(legend.position='none')
ggsave('test_trial_path.pdf', path='/home/prez/tmp/cheeseboard', 
       device = cairo_pdf, units='cm', width=3.7, height=3.6)
```


Velocity not different inside and outside of reward zone
```{r}
test.trial.velocities = test.trial.df %>%
  dplyr::select(date, animal, day_desc, mroi_velocity, moutside_roi_velocity) %>%
  pivot_longer(cols=c(mroi_velocity, moutside_roi_velocity),
               names_to='location',
               values_to='velocity') %>%
  filter(!is.na(velocity), velocity < Inf) %>%
  mutate(aday=paste(animal, day_desc, sep='_'))

test.trial.velocities$location = as.factor(test.trial.velocities$location)
test.trial.velocities$aday = as.factor(test.trial.velocities$aday) %>% as.integer() %>% as.factor()

test.trial.velocities %>%
  ggplot(aes(x=location, y=velocity*perc2dist)) +
  geom_violin(draw_quantiles = c(0.5)) +
  geom_jitter(height=0, width=0.3, shape=1, alpha=0.6) +
  ylim(c(0, 35)) +
  ylab('Velocity (cm/s)') +
  gtheme

lmer.test.print(test.trial.velocities %>%
                  filter(!is.na(velocity), velocity < Inf),
                var=velocity,
                fixed.effects = location,
                diagnostics.groupvar = 'animal',
                randef.str = '(1 | aday)')

bf.models = create.bayes.lm.pair(test.trial.velocities,
                                 formula.full = velocity ~ location + aday,
                                 formula.null = velocity ~ aday,
                                 whichRandom = c('aday'))
bf.models$full / bf.models$null
```

