---
title: "R Notebook"
output: html_notebook
---

```{r library setup}
library(dplyr)
library(plyr)
library(pracma)
library(readr)
library(tidyr)
library(tibble)
library(stringr)
library(DT)
library(data.table)
library(permute)
#library(doParallel)
#library(foreach)
library(tictoc)

library(ggplot2)
library(cowplot)
gtheme = theme_minimal() + theme_cowplot() +
  theme(text = element_text(size=18), axis.text = element_text(size=15))

summarise = dplyr::summarise
summarize = dplyr::summarize

source('locations.R')
```

```{r data dirs setup}
nbins = 20

root_dir07 = '/mnt/DATA/Prez/cheeseboard-down/down_2/2019-07/'
root_dir08 = '/mnt/DATA/Prez/cheeseboard-down/down_2/2019-08/'
rootdirs = c(root_dir07, root_dir08)
gen_imgs_dir = '/mnt/DATA/Prez/pf_stability/'

caimg_result_dirs = c(
  #get.subject.result.dirs(root_dir08, 'E-BL'),
  #get.subject.result.dirs(root_dir08, 'E-TR'),
  #get.subject.result.dirs(root_dir08, 'F-BL'),
  #get.subject.result.dirs(root_dir08, 'F-TL'),
  get.subject.result.dirs(root_dir07, 'A-BL'),
  get.subject.result.dirs(root_dir07, 'B-BL'),
  get.subject.result.dirs(root_dir07, 'C-1R'),
  get.subject.result.dirs(root_dir07, 'D-BR')
)

caimg_result_dirs = Filter(
  function(ca_img_dir) {file.exists(paste(ca_img_dir, 'traces_and_positions.csv', sep='/'))},
  caimg_result_dirs)

```

Read rewards locations
```{r}
all.locations.df = map_dfr(rootdirs, read_locations)
rewards.df =  all.locations.df %>%
  filter(!is_test) %>%
  dplyr::rename(animal=Animal) %>%
  left_join(mouse.meta.df, by='animal') %>% 
  left_join(trials.meta.df, by=c('date', 'animal', 'location_set'))
```



```{r}
fr.hz = 20

calc.reward.info = function(data.traces) {
  data.traces = data.table(data.traces)
  data.traces = data.traces[x >= 0 & y >= 0, ]
  
  timebinned.traces = timebin.traces(data.traces, timebin.dur.msec = 200)
  bin.quantile.fractions = c(0.95, 1.0)
  binned.traces = bin.responses(timebinned.traces, 
                                get.bin.thresholds.fun = get.quantiles.fun(bin.quantile.fractions),
                                binned.var='trace')
  binned.traces[,  atAnyReward := ifelse(atReward0 + atReward1 > 0, 1, 0)]
  binned.traces[, atReward0 := ceil(atReward0)]
  binned.traces[, atReward1 := ceil(atReward1)]
  cells = unique(binned.traces$cell_id) %>% sort
  
  res = data.frame()
  for (cell_name in cells) {
    cell.df = binned.traces[cell_id == cell_name,]
    trace.vals = cell.df[['response_bin']] %>% as.integer()
    trial.ends = get.trial.ends(cell.df$timestamp)
    
    mi_anyreward = mutual_info_with_shuffles(
      trace.vals,
      nresponseBins=length(bin.quantile.fractions),
      cell.df$atAnyReward + 1, 
      nstim=2,
      trial.ends,
      nshuffles=100,
      shuffleChunkLength=2*fr.hz)
    mi_anyreward.signif.thresh = quantile(mi_anyreward$shuffle.mi, 0.95, na.rm=TRUE)[[1]]
    anyreward.mfr_model = create_mfr_model(cell.df$atAnyReward + 1, 2, cell.df$nevents, minOccupancy=10)
    
    mi_onereward = mutual_info_with_shuffles(
      trace.vals,
      cell.df$atReward0 + cell.df$atReward1 * 2 + 1,
      trial.ends,
      nresponseBins=length(bin.quantile.fractions),
      nstim=3,
      nshuffles=100,
      shuffleChunkLength=2*fr.hz)
    onereward.mfr_model = create_mfr_model(cell.df$atReward0 + cell.df$atReward1 * 2 + 1, 3, 
                                           cell.df$nevents, minOccupancy=10)
    mi_onereward.signif.thresh = quantile(mi_onereward$shuffle.mi, 0.95, na.rm=TRUE)[[1]]
    
    cell_info = list(cell_id=cell_name,
                     date=cell.df$date[[1]],
                     animal=cell.df$animal[[1]],
                     mi.anyrew = mi_anyreward[['mutual.info']],
                     mi.anyrew.bias = mi_anyreward[['mutual.info.bias']],
                     mi.anyrew.signif.thresh = mi_anyreward.signif.thresh,
                     mi.anyrew.signif = mi_anyreward[['mutual.info']] > mi_anyreward.signif.thresh,
                     mfr.norew = anyreward.mfr_model$fr[1],
                     mfr.anyrew = anyreward.mfr_model$fr[2],
                     mi.onerew = mi_onereward[['mutual.info']],
                     mi.onerew.bias = mi_onereward[['mutual.info.bias']],
                     mi.onerew.signif.thresh = mi_onereward.signif.thresh,
                     mi.onerew.signif = mi_onereward[['mutual.info']] > mi_onereward.signif.thresh,
                     mfr.rew0 = onereward.mfr_model$fr[2],
                     mfr.rew1 = onereward.mfr_model$fr[3],
                     mfr=mean(cell.df$nevents))
    res = bind_rows(res, cell_info)
  }
  
  return(res)
}
```

```{r}
locations.rootdir = "/mnt/DATA/Prez/cheeseboard/2019-08/"
rewards.df = read_locations(locations.rootdir) %>%
  filter(!is_test) %>%
  dplyr::rename(animal=Animal)
```


```{r}
trial.reward.info = data.frame()

for (ca_img_result_dir in caimg_result_dirs) {
  dir_parts = str_split(ca_img_result_dir, '/')
  animal_name = dir_parts[[1]][length(dir_parts[[1]]) - 2]
  date_str = dir_parts[[1]][length(dir_parts[[1]]) - 4]
  rewards.subset = filter(rewards.df, date==date_str, animal==animal_name)
  if (nrow(rewards.subset) > 0) {
    print(paste('Processing dir: ', ca_img_result_dir))
    data.traces = read.data.trace(caimg_result_dir, filter_exp_title='trial')
    detect.events(data.traces, deconv.threshold=0.2)
    
    tic('Calculation of reward mutual information')
    reward.info.df = calc.reward.info(data.traces)
    trial.reward.info = bind_rows(trial.reward.info, reward.info.df)
    toc()
  }
}
```

Distribution of reward mutual information
```{r}
trial.reward.info %>%
  ggplot() +
  geom_violin(aes(x=date,y=mi.anyrew-mi.anyrew.bias, color=mi.anyrew.signif)) +
  #geom_violin(aes(x=date,y=mi.onerew-mi.onerew.bias, color=mi.onerew.signif)) +
  gtheme +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

How many of them are place cells when running?
```{r}
trial.reward.pc = left_join(trial.reward.info, place.cell.db, by=c('date', 'animal', 'cell_id'))
```


```{r}
trial.reward.pc %>%
  mutate(active.rew = mfr.anyrew > mfr.norew,
         active.rew0 = mfr.rew0 > mfr.norew,
         active.rew1 = mfr.rew1 > mfr.norew,
         is.rew.pc = is.pc & active.rew) %>%
  group_by(date) %>%
  dplyr::summarise(anyrew.n = (sum(mi.anyrew.signif) / n() * 100) %>% round,
                   anyrew.active.n = (sum(mi.anyrew.signif & active.rew) / n() * 100) %>% round,
                   pc.n = (sum(is.pc) / n()  * 100) %>% round,
                   #rew.pc.n = sum(is.rew.pc) / n(),
                   anyrew.pc.n = (sum(mi.anyrew.signif & is.rew.pc) / n() * 100) %>% round,
                   onerew.n = (sum(mi.onerew.signif) / n() * 100) %>% round,
                   onerew.active.n = (sum(mi.onerew.signif & (active.rew0 | active.rew1)) / n() * 100) %>% round,
                   onerew.pc.n = (sum(mi.onerew.signif & is.rew.pc) / n() * 100) %>% round)
                   
  
```
Close to 30 % of cells active at reward, only 3-5 % of them are place cells. However these cells seem to be variable between trials as seen on the place fields.
Could be SWRs related..


- What if split time at reward into parts: level of activity vs time at reward. Need to look at population firing to see the timing of firing at reward.
