---
title: "Cheeseboard learning analysis"
output:
  html_document:
    df_print: paged
---


```{r imports}
library(dplyr)
library(ggplot2)
library(cowplot)
library(readr)
library(tidyr)

source('crossings.R')
source('distances.R')
source('locations.R')
source('tracking_files.R')
```

```{r}
dir = '/mnt/DATA/Prez/cheeseboard/2019-02-learning'
hab_dir = '/mnt/DATA/Prez/cheeseboard/2019-02-habituation'
df = read_csv(paste0(dir, '/trial_stats.csv'))
locations.df = read_locations(dir)

frame.hz = 24
```

```{r}
library(cowplot)
gtheme = theme_minimal() + theme_cowplot() + 
  theme(text = element_text(size=18), axis.text = element_text(size=15)) 
```

Filter invalid trials (e.g. no reward on the maze..)
```{r}
invalid_df = read_csv(paste0(dir, '/invalid_trials.csv'))
df = left_join(df, invalid_df, by = c('date', 'animal_id', 'trial_n', 'is_test'), suffix=c('', '.y')) %>%
  filter(is.na(invalid) || invalid == FALSE)
```
```{r}
df = df %>%
  mutate(total_trial_n=6*(learning_day1 - 1) + trial_n) 
```


```{r}
notest.df = filter(df, !is_test)
```

Total distance travelled
```{r}
d = notest.df 
d$learning_day1 = as.factor(d$learning_day1)

gdist = d %>%
  filter(time_finished > 0) %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1, y=total_dist/100)) +
  #geom_jitter(aes(x=learning_day1, y=mdist/100, color=animal_id),height=0, width=0.1, size=1) +
  geom_point(aes(x=learning_day1, y=total_dist/100, color=animal_id), size=2) +
  gtheme +
  xlab('Training day') +
  ylim(c(0,20)) +
  ylab('Total distance') +
  geom_hline(yintercept=1, linetype="dashed", color = "black") +
  geom_vline(xintercept=7.5, linetype="dashed", color = "red") +
  geom_vline(xintercept=11.5, linetype='dashed', color='blue') +
  geom_vline(xintercept=15.5, linetype='dashed', color='red') +
  ylim(c(0, 15)) +
  gtheme+
  theme(legend.position = 'none')
gdist

ggsave(paste0(gen_imgs_dir, 'learning_dist.svg'), width=7, height=4)
```

In day learning based on total distance
```{r}

```


Duration of the trials
```{r}
gdur = d %>%
  filter(time_finished > 0) %>%
  #group_by(animal_id,learning_day1) %>%
  #summarise(mdur=mean(total_frames/frame.hz)) %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1, y=time_finished)) +
  #geom_jitter(aes(x=learning_day1, y=mdur, color=animal_id),height=0, width=0.1, size=1) +
  geom_point(aes(x=learning_day1, y=time_finished, color=animal_id),height=0, width=0.1, size=1) +
  gtheme +
  geom_vline(xintercept=8.5, linetype='dashed', color='red') +
  geom_vline(xintercept=11.5, linetype='dashed', color='blue') +
  xlab('Training day') +
  ylab('Trial time (sec)') +
  ylim(c(0,200))
gdur
ggsave(filename='gdist.svg', plot=gdist, width=5)
ggsave(filename='gdur.svg', plot=gdur, width=5)
```

Total number of crossings
```{r}
ggplot(d) +
  geom_boxplot(aes(x=learning_day1, y=crossings_n)) +
  ylim(c(0,10))
```

Total distance travelled per mouse
```{r}
d %>% 
  filter(time_finished > 0) %>%
  group_by(animal_id, learning_day1) %>%
  summarise(mdist=mean(total_dist), sddist=sd(total_dist), mdur=mean(total_frames/frame.hz), sddur=sd(total_frames/frame.hz)) %>%
  ggplot() +
  geom_line(aes(x=learning_day1, y=mdist, group=animal_id, color=animal_id)) 
  #geom_ribbon(aes(x=learning_day1, ymin=mdist-sddist, ymax=mdist+sddist, group=animal_id, fill=animal_id), alpha=0.1)

```

Diff from optimal path
```{r}
path_len = function(points) {
  len = 0
  xdiff = diff(points$x)
  ydiff = diff(points$y)
  for (i in 1:length(xdiff)) {
    len = len + sqrt(xdiff[i]^2 + ydiff[i]^2)
  }
  return(len)
}

as.percent = function(x, y) {
  return (x - y / y * 100)
}

d2 = d %>% 
  rowwise() %>%
  mutate(min_path1=path_len(list(x=c(start_x, rew1_x, rew2_x), y=c(start_y, rew1_y, rew2_y))),
         min_path2=path_len(list(x=c(start_x, rew2_x, rew1_x), y=c(start_y, rew2_y, rew1_y))),
         min_path=ifelse(min_path1<min_path2, min_path1, min_path2),
         norm_dist=total_dist / min_path * 100)
         
gdist = d2 %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1, y=norm_dist/100)) +
  #geom_jitter(aes(x=learning_day1, y=mdist/100, color=animal_id),height=0, width=0.1, size=1) +
  geom_point(aes(x=learning_day1, y=norm_dist/100, color=animal_id), size=2) +
  gtheme +
  xlab('Training day') +
  ylab('Norm. distance') +
  ylim(c(0,20))+
  geom_hline(yintercept=1, linetype="dashed", color = "black") +
  geom_vline(xintercept=7.5, linetype="dashed", color = "red") +
  geom_vline(xintercept=11.5, linetype='dashed', color='blue') +
  geom_vline(xintercept=15.5, linetype='dashed', color='red') 

gdist
```

```{r}
d2 %>%
  group_by(learning_day1) %>%
  summarise(m.norm_dist=median(norm_dist), sd.norm_dist=sd(norm_dist))
```

Is running to the closer reward first? Would confirm model-based learning
```{r}
which.rew.df = d %>%
  filter(time_finished > 0) %>%
  rowwise() %>%
  mutate(dist_rew1=path_len(list(x=c(start_x, rew1_x), y=c(start_y, rew1_y))),
         dist_rew2=path_len(list(x=c(start_x, rew2_x), y=c(start_y, rew2_y))),
         closer_rew=which.min(c(dist_rew1, dist_rew2)),
         run_closer=(closer_rew == which.min(c(passed_rew0, passed_rew1))))

which.rew.df %>%
  group_by(learning_day1, animal_id) %>%
  summarise(shorter_run_pct = sum(run_closer) / n()) %>%
  ggplot() +
  geom_point(aes(x=learning_day1, y=shorter_run_pct, colour=animal_id))
         
```


Time at reward
```{r}

d2 %>% 
  group_by(animal_id, learning_day1) %>%
  summarise(mdist=mean(norm_dist), 
            sddist=sd(norm_dist),
            mrew_dwell_pct=mean(rew_dwell_pct),
            sdrew_dwell_pct=sd(rew_dwell_pct),
            mdur=mean(total_frames/frame.hz), 
            sddur=sd(total_frames/frame.hz)) %>%
  ggplot() +
  geom_line(aes(x=learning_day1, y=mrew_dwell_pct, group=animal_id, color=animal_id)) 

gdwell = d2 %>%
  group_by(learning_day1, animal_id) %>%
  summarise(mrew_dwell_pct=mean(rew_dwell_pct),
            sdrew_dwell_pct=sd(rew_dwell_pct)) %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1, y=mrew_dwell_pct)) +
  geom_point(aes(x=learning_day1, y=mrew_dwell_pct), size=1) +
  geom_vline(xintercept=7.5, linetype="dashed", color = "blue") +
  xlab('Training day') + ylab('Time at reward (%)') +
  gtheme
gdwell
```

```{r}
d2 %>%
  group_by(learning_day1) %>%
  summarise(mrew_dwell_pct=mean(rew_dwell_pct), sdrew_dwell_pct=sd(rew_dwell_pct))
```


Time of dwelling at reward
```{r}
gdwell = d2 %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1, y=rew_dwell_pct)) +
  geom_point(aes(x=learning_day1, y=rew_dwell_pct)) +
  #geom_jitter(aes(x=learning_day1, y=rew_dwell_pct, color=animal_id),height=0, width=0.1, size=3) +
  xlab('Training day') +
  ylab('Time at reward (%)') +
  geom_vline(xintercept=11.5, linetype="dashed", color = "blue") +
  gtheme
gdwell
ggsave(filename='gdwell.svg', plot=gdwell, width=5)
```
Dwell Time in trial tests
```{r}
df %>%
  mutate(learning_day1_f = as.factor(learning_day1)) %>%
  filter(is_test) %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1_f, y=rew_dwell_pct))

df %>%
  filter(is_test) %>%
  group_by(learning_day1) %>%
  summarise(mdwell=mean(rew_dwell_pct),sddwell=sd(rew_dwell_pct))
```

# Number of crossings in trial tests
```{r}
test.trial.df = df %>%
  mutate(learning_day1_f = as.factor(learning_day1)) %>%
  mutate(crossings_0_60s=crossings_0_30s+crossings_30_60s) %>%
  mutate(crossings_per_min=crossings_n/(total_frames/frame.hz) * 60) %>%
  mutate(norm_crossings=crossings_0_30s * 100.0 / dist_30s) %>%
  filter(is_test) 

gcross = test.trial.df %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1_f, y=crossings_0_60s)) +
  geom_jitter(aes(x=learning_day1_f, y=crossings_0_60s, color=animal_id), height=0, width=0.1, size=3) +
  xlab('Test day') +
  ylab('# Crossings during 60s') + 
  gtheme +
  theme(legend.position='None') 
gcross
ggsave(filename='gcross.svg', plot=gcross, width=3)

gcross.ratio = test.trial.df %>%
  ggplot() +
  geom_boxplot(aes(x=learning_day1_f, y=crossings_0_60s/(dist_60s/20.0/25)), outlier.size=0) +
  geom_jitter(aes(x=learning_day1_f, y=crossings_0_60s/(dist_60s/20.0/25), color=animal_id),height=0, width=0.1, size=3) +
  xlab('Test day') +
  ylab('# Crossings / \n# Crossings in random \nexploration') +
  gtheme +
  theme(legend.position='None') 
  
gcross.ratio
ggsave(filename='gcross_ratio.svg', plot=gcross.ratio, width=3)
```


Calculate number of crossings during habituation for each location set
```{r, warning=FALSE}
hab.files = get_tracking_files(hab_dir)
animal.locations = locations.df %>%
  mutate(rowxcol=paste0(as.character(Well_row), 'x', as.character(Well_col))) %>%
  filter(Valence == 'Positive') %>%
  filter(is_test == FALSE) %>%
  group_by(Animal, rowxcol, location_set) %>%
  select(Animal, rowxcol, Well_row, Well_col, trans_x, trans_y, location_set)

hab_loc=full_join(hab.files, animal.locations, by=c("animal"="Animal"))
hab_loc$crossings = rep(0, nrow(hab_loc))
hab_loc$total_dist = rep(0, nrow(hab_loc))
hab_loc$total_frames = rep(0, nrow(hab_loc))
for (i in 1:nrow(hab_loc)) {
  tracking.df = read_csv(hab_loc$filepath[i], col_types = cols())
  tracking.df.filtered = filter(tracking.df, trans_x >= 0, trans_y >= 0)
  crossings = crossings4positions(
                      tracking.df.filtered$smooth_trans_x, tracking.df.filtered$smooth_trans_y, 
                      hab_loc$trans_x[i], hab_loc$trans_y[i], 10)
  hab_loc$crossings[i] = crossings
  frame_60s = frame.hz*60
  hab_loc$crossings_0_60s = crossings4positions(
                      tracking.df.filtered$smooth_trans_x[1:frame_60s], tracking.df.filtered$smooth_trans_y[1:frame_60s], 
                      hab_loc$trans_x[i], hab_loc$trans_y[i], 10)
  distances = vec_dist(tracking.df.filtered$smooth_trans_x, tracking.df.filtered$smooth_trans_y)
  hab_loc$total_dist[i] = sum(distances)
  hab_loc$total_frames[i] = last(tracking.df.filtered$frame) - first(tracking.df.filtered$frame)
}

```
Average across different trials
```{r}
hab_loc = mutate(hab_loc, norm_crossings = crossings * 100.0 / total_dist)
mhab_loc = hab_loc %>%
  group_by(animal, location_set) %>%
  summarise(mnorm_crossings = mean(norm_crossings) * 2,
            mcrossings_0_60s = mean(crossings_0_60s) * 2) %>%
  rename(norm_crossings=mnorm_crossings, crossings_0_60s=mcrossings_0_60s, animal_id=animal) %>%
  mutate(type="habituation")
```

Compare crossings in probe tests vs habituation
```{r}
mhab_loc.filtered = mhab_loc %>% filter(animal_id %in% unique(test.trial.df$animal_id))
mhab_loc.perdate = test.trial.df %>%
  dplyr::select(animal_id, location_set, date) %>%
  left_join(mhab_loc.filtered, by=c('animal_id', 'location_set'))

test.trial.df.joined = test.trial.df %>%
  select(animal_id, location_set, date, norm_crossings, crossings_0_60s) %>%
  mutate(type="test")  %>%
  bind_rows(mhab_loc.perdate)

test.trial.df.joined$type = as.factor(test.trial.df.joined$type)
test.trial.df.joined$location_set = as.factor(test.trial.df.joined$location_set)

test.trial.df.joined = test.trial.df.joined %>%
  mutate(paired_group=interaction(date, type, lex.order=TRUE),
         group_id=interaction(date, animal_id))
test.trial.df.joined$paired_group = as.factor(test.trial.df.joined$paired_group)
test.trial.df.joined$paired_group_num=as.integer(test.trial.df.joined$paired_group)
```

```{r}
ntests = length(unique(test.trial.df$date))
gcross.compare = ggplot(test.trial.df.joined, aes(x=paired_group_num, y=norm_crossings)) +
  #geom_boxplot(aes(x=paired_group_num, group=paired_group_num, fill=type), notch=FALSE) +
  geom_point(size=3, aes(color=type)) +
  geom_line(aes(group=group_id), size=0.3, alpha=0.4) + 
  xlab('Test date') +
  ylab('# Crossings / distance') +
  labs(fill='') + 
  scale_x_continuous(breaks=seq(1,ntests*2,2)+0.5, labels=1:ntests) +
  gtheme + theme(legend.position="top")
gcross.compare
ggsave(paste0(gen_imgs_dir, 'crossings.svg'), width=4, height=4)
```

Statistically significant difference
```{r}
wilcox.test(norm_crossings ~ type, data=test.trial.df.joined, subset=location_set==1, paired=TRUE)
animal.ids2 = subset(test.trial.df.joined, type=='test' & location_set==2, select=animal_id)
df=filter(test.trial.df.joined, location_set==2) %>% filter(animal_id %in% animal.ids2$animal_id)
wilcox.test(norm_crossings ~ type, data=df, paired=TRUE)
```

```{r}


# Paired comparisons of crossings counts
gcross.paired.absolute = test.trial.df.joined %>%
  select(animal_id, date, location_set, crossings_0_60s, type) %>%
  spread(type, crossings_0_60s) %>%
  mutate(cross_diff = test-habituation) %>%
  ggplot() +
  #geom_boxplot(aes(x=location_set, y=cross_diff)) +
  geom_dotplot(aes(x=location_set, y=cross_diff, fill=animal_id), binaxis='y', dotsize=2) +
  xlab('Reward location set') +
  ylab('Increase in #crossings (60s)\nafter learning vs habituation') +
  ylim(c(0,8)) +
  gtheme 

gcross.paired.absolute
```

```{r}
cg.stats=plot_grid(gdist, gdwell, gcross.compare, 
                   labels=c('B', 'C', 'D'), 
                   ncol=3,
                   label_size=25,
                   label_fontface='bold')
cg.stats
ggsave(filename='gstats.svg', plot=cg.stats, width=10, height=3.5)
```


# Change of reward location

Within day improvement -- early trials on a given day have more crossings of the previous reward location
```{r}
prev.reward.d = filter(d, !is.na(ncross_prev_rew))

ggplot(prev.reward.d)%>% +
  #geom_jitter(aes(x=learning_day1, y=ncross_prev_rew, color=animal_id), width=0.2)
  #geom_jitter(aes(x=trial_id, y=ncross_prev_rew, color=animal_id), width = 0, height=0.3, size=2)
  geom_point(aes(x=trial_id, y=ncross_prev_rew, color=animal_id), size=2)
```

# Aversive zone learning

```{r}
airpuff.dates = filter(locations.df, Valence == 'Negative', is_test==FALSE) %>%
  select(date) 
airpuff.dates = unique(airpuff.dates$date) %>% as.Date
puff.d = filter(d, date %in% airpuff.dates)
```


Crossings
```{r}
library(Hmisc)
puff.d %>%
  filter(learning_day < 17) %>%
  ggplot(aes(x=learning_day1, y=nroi_crossings)) +
  geom_boxplot(aes(color=animal_id)) +
  gtheme +
  theme(legend.position = 'none') +
  ylim(c(0,3)) +
  xlab('Learning Day') +
  ylab('# Air puff zone crossings')
```
Future crossings
```{r}
future.crossings.df = filter(d, is_test==FALSE, !is.na(ncross_future_roi))
future.crossings.df %>%
  group_by(learning_day1, animal_id) %>%
  summarise(mcross_roi = mean(ncross_future_roi))
```


Duration in ROI
```{r}
puff.d %>%
  filter(learning_day < 17) %>%
  ggplot(aes(x=learning_day1, y=roi_duration/1000)) +
  geom_boxplot(aes(color=animal_id)) +
  gtheme +
  theme(legend.position='none')  +
  ylab('Air puff duration (sec)') + xlab('Learning Day') 
ggsave(paste0(gen_imgs_dir, 'air_puff_dur.png'), width=5, height=4)
  
```


Velocity through ROI
```{r}
puff.d %>%
  filter(!is.na(mroi_velocity)) %>%
  ggplot(aes(x=learning_day1, y=mroi_velocity/mvelocity)) +
  #geom_jitter(aes(color=animal_id),height=0, width=0.1)
  stat_summary(fun.data = "mean_cl_boot", geom='point', mapping=aes(group=animal_id, color=animal_id))

```

