---
title: "R Notebook"
output: html_notebook
---


```{r setup} 
library(dplyr)
library(plyr)
library(pracma)
library(purrr)
library(readr)
library(tidyr)
library(tibble)
library(smoothie)
library(stringr)
library(DT)
library(data.table)
library(datatrace)

library(ggplot2)
library(cowplot)
gtheme = theme_minimal() + theme_cowplot() +
  theme(text = element_text(size=10), axis.text = element_text(size=8))

summarise = dplyr::summarise
summarize = dplyr::summarize
```

Setup example variables
```{r}
nbins = 30
animal_name = 'E-TR'
exp_title='learning'
day = '2019-08-31'
cell_name = 51
```



```{r}
geom_rewards = function(rewards.df, subject=NULL, day=NULL, nbins=20) {
  dayreward.df = rewards.df
  if (!is.null(subject)) {
    dayreward.df = filter(rewards.df, animal==subject)
  }
  if (!is.null(day)) {
    dayreward.df = filter(dayreward.df, date==day)
  }
  if (!('current_loc' %in% names(dayreward.df))) {
    dayreward.df$current_loc = TRUE
  }
  dayreward.df = dplyr::mutate(
    dayreward.df,
    rew_name = ifelse(current_loc, 'current_rew', 'prev_rew'))
  rew.colours = c('prev_rew'='gray60', 'current_rew'='white', 'TRUE'='red', 'FALSE'='blue')
  #rew.shape = 0
  rew.shape = 2
  rew.size = 2
  bin.size = 100 / nbins
  list(geom_point(data=dayreward.df, 
                  aes(x=trans_x / bin.size, y=(100 - trans_y) / bin.size, color=rew_name), 
                  shape=rew.shape,
                  size=rew.size,
                  stroke=2),
       scale_color_manual(values=rew.colours))
}

all.locations.df = map_dfr(rootdirs, read_locations)
rewards.df =  all.locations.df %>%
  filter(!is_test) %>%
  left_join(mouse.meta.df, by='animal') %>% 
  left_join(trials.meta.df, by=c('date', 'animal', 'location_set'))
```

```{r}

f1 = odd.fields[[animal_name]][[day]][[paste(cell_name)]]
oc1 = odd.occupancies[[animal_name]][[day]][[paste(cell_name)]]

f2 = even.fields[[animal_name]][[day]][[paste(cell_name)]]
oc2 = even.occupancies[[animal_name]][[day]][[paste(cell_name)]]
odd.field = create.pf.df(f1, oc1)
even.field = create.pf.df(f2, oc2)

oddeven.cor = field.cor(odd.field, even.field, make.cor.plot=TRUE, max.xy=nbins)
cor.title = paste0('Odd vs Even cor=', format(oddeven.cor$cor, digits=2))
oddeven.cor$g + labs(title=cor.title, fill='Correlation')

```


```{r}

plot.field.comparison = function(animal_name, day, cell_name, plot.dir=NA) {
  odd.pf = create.partial.df(odd.fields, odd.occupancies, animal_name, day, cell_name, 'Odd')
  even.pf = create.partial.df(even.fields, even.occupancies, animal_name, day, cell_name, 'Even')
  early.pf = create.partial.df(early.fields, early.occupancies, animal_name, day, cell_name, 'Early')
  late.pf = create.partial.df(late.fields, late.occupancies,  animal_name, day, cell_name, 'Late')
  
  cell.row = run.trials.pc %>% filter(animal==animal_name, date==day, cell_id==cell_name)
  
  text.theme = theme(text = element_text(size=10),
                     plot.title = element_text(size=10))
  
  g.placefield = bind_rows(odd.pf, even.pf, early.pf, late.pf) %>%
    plot.pf(max.x=nbins, max.y=nbins) +
    facet_wrap(. ~ group, ncol = 2) +
    geom_rewards(rewards.df, animal_name, day, nbins) +
    labs(title=paste0(animal_name,
                      ', ', day,
                      ', cell ', cell_name, 
                      '\nSI = ', format(cell.row$spatial.information, digits=2), ' bits/s',
                      ifelse(cell.row$signif.si, ' *', ''),
                      ', ', format(cell.row$spatial.information.perspike, digits=2), ' bits/spike',
                      '\nMI - bias = ', format(cell.row$mutual.info - cell.row$mutual.info.bias, digits=3),
                      ifelse(cell.row$signif.mi, '*', ''),
                      '\nsparsity = ', format(cell.row$sparsity, digits=2)),
         fill='Deconv\ntrace') +
    text.theme

  
  oddeven.cor = field.cor(odd.pf, even.pf, make.cor.plot=TRUE, max.xy=nbins)
  cor.title = paste0('cor=', format(oddeven.cor$cor, digits=2))
  g.oddeven.cor = oddeven.cor$g + labs(title=cor.title, fill='') + 
    geom_rewards(rewards.df, animal_name, day, nbins) + text.theme
  
  earlylate.cor = field.cor(early.pf, late.pf, make.cor.plot=TRUE, max.xy=nbins)
  cor.title = paste0('cor=', format(earlylate.cor$cor, digits=2))
  g.earlylate.cor = earlylate.cor$g + labs(title=cor.title, fill='') + 
    geom_rewards(rewards.df, animal_name, day, nbins) + text.theme +
    theme(legend.position='none')
  
  g.cors = plot_grid(g.earlylate.cor, g.oddeven.cor, ncol=2, rel_widths=c(1, 1.7))
  
  g = plot_grid(g.placefield, g.cors, ncol=1, rel_heights=c(2,1))
  if (!is.na(plot.dir)) {
    if (cell.row$is.pc) {
      plot.subdir = file.path(plot.dir, 'place_cell')
    } else if (cell.row$is.pc) {
      plot.subdir = file.path(plot.dir, 'signif')
    } else {
      plot.subdir = file.path(plot.dir, 'other')
    }
    dir.create(plot.subdir, recursive=TRUE)
    fname = paste0('place_field_cell_', cell_name, '.jpg')
    ggsave(file.path(plot.subdir, fname), 
           g,
           width=5.5, height=8, units='cm', dpi=300)
  }
  return(g)
}
```


```{r}
plot.dir = file.path('/tmp/pf_stability/', animal_name, day)
plot.field.comparison(animal_name, day, cell_name, plot.dir=plot.dir)
```

```{r}
save.field.comparison = function(animal_name, day, cell_name) {
  plot.dir = file.path('/mnt/DATA/Prez/pf-daystability', animal_name, day)
  plot.field.comparison(animal_name, day, cell_name, plot.dir)
  return(1)
}

run.trials.si %>%
  select(animal, date, cell_id) %>%
  distinct() -> tmp.df

for (i in 1:nrow(tmp.df)) {
   tryCatch({save.field.comparison(tmp.df$animal[i],
                                   tmp.df$date[i],
                                   tmp.df$cell_id[i])},
  error=function(e){cat("ERROR for row i=", num2str(i), ":",conditionMessage(e), "\n")})
}
```


# Plots on example trace
Load the traces
```{r}
# animal_name = 'F-TL'
# exp_title='learning'
# day = '2019-09-04'
# root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2019-08/'
animal_name = 'F-TL'
exp_title='learning'
day = '2019-09-04'
root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2019-08/'


caimg_result_dir = file.path(root_dir, exp_title, day, 'caiman', animal_name, 'filtered/')
data.traces = read.data.trace(caimg_result_dir)
setorder(data.traces, trial_id, cell_id, timestamp)
data.traces$is_running = isRunning(data.traces, 2, 4, 500)
data.traces = as.data.table(data.traces)
detect.events(data.traces, deconv.threshold=0.2)
data.traces.run = data.traces[(is_running), ]

```

## Event vectors and place fields of the cell for each trial 
```{r}
frame.rate = 1000 / 200

plot.cell.trials = function(cell.df, trace.var='trace', facet.ncols=3) {
  if (nrow(cell.df) == 0) {
    return(ggplot(data.frame()))
  }
  animal_name = cell.df$animal[1]
  day = cell.df$date[1]
  trials = unique(cell.df$trial)
  
  trials.spatial = c()
  merged.pf.df = data.frame()
  calc.place.field = function(cell.df, min.occupancy.sec=10, nshuffles=0) {
    pf = cell.spatial.info(cell.df,
                           nbins, nbins,
                           trace.var = trace.var,
                           generate.plots=FALSE,
                           nshuffles=nshuffles,
                           min.occupancy.sec=min.occupancy.sec)
    pf.df = create.pf.df(pf$field, pf$occupancy, 
                         frame.rate=frame.rate,
                         min.occupancy.sec=min.occupancy.sec)
    list(df=pf.df,pf=pf)
  }
  
  for (trial_no in trials) {
    pf.df = calc.place.field(cell.df[trial == trial_no & exp_title == 'trial', ],
                                min.occupancy.sec = 0.1)$df
    pf.df$trial = num2str(trial_no, fmt=0)
    merged.pf.df = bind_rows(merged.pf.df, pf.df)
  }
  
  aftertest.df = cell.df[exp_title == 'aftertest', ]
  if (nrow(aftertest.df) > 0) {
    pf.df = calc.place.field(aftertest.df,
                             min.occupancy.sec=0.1, 
                             nshuffles=0)$df
    pf.df$trial = 'aftertest'
    merged.pf.df = bind_rows(merged.pf.df, pf.df)
  }
  beforetest.df = cell.df[exp_title == 'beforetest', ]
  if (nrow(beforetest.df) > 0) {
    pf.df = calc.place.field(beforetest.df,
                             min.occupancy.sec=0.1, 
                             nshuffles=0)$df
    pf.df$trial = 'beforetest'
    merged.pf.df = bind_rows(merged.pf.df, pf.df)
  }
    
  all.trials.pf = calc.place.field(cell.df[exp_title == 'trial', ],
                                   min.occupancy.sec=1, 
                                   nshuffles=1000)
  all.trials.pf$df$trial = 'all_trials'
  merged.pf.df = bind_rows(merged.pf.df, all.trials.pf$df)
  
  
  cell_info = all.trials.pf$pf$cell_info
  g = plot.pf(merged.pf.df, max.x=nbins, max.y=nbins) +
    geom_rewards(prev.locations.df, animal_name, day, nbins) +
    facet_wrap(. ~  trial, ncol=facet.ncols) +
    labs(fill=paste(trace.var, 'values'),
         title=paste0(format(day), ' ', animal_name, ' Cell ', cell_name, 
                      '\nSI = ', format(cell_info$spatial.information, digits=2),
                      ifelse(cell_info$signif.si, '*', ''),
                      ' SI per spike = ', format(cell_info$spatial.information.perspike, digits=2),
                      '\nMI - bias = ', format(cell_info$mutual.info - cell_info$mutual.info.bias, digits=3),
                      ifelse(cell_info$signif.mi, '*', '')))
  
  
  print(all.trials.pf$pf$cell_info$spatial.information)
  print(all.trials.pf$pf$cell_info$mutual.info)
  print(all.trials.pf$pf$cell_info$mfr)
  return(g)
}

cell_name = 183
cell.df = data.traces.run[cell_id == cell_name & x >= 0 & y >= 0, ]
binned.cell.df = bin.time.space(cell.df, 
                                nbins.x = nbins,
                                nbins.y = nbins,
                                get.bin.thresholds.fun=get.quantiles.fun(c(0.95, 1.0)),
                                binned.var='deconv_trace',
                                timebin.dur.msec=200)
binned.cell.df[,is_running:=as.logical(is_running)]

gen_imgs_dir = '/home/prez/tmp/cheeseboard/'
plot.cell.trials(binned.cell.df, trace.var='deconv_trace', facet.ncols=5)
ggsave(file.path(gen_imgs_dir, paste0(cell_name, '_place_fields.svg')),
       width=23, height=8, units='cm')

binned.cell.df[, trial_name := paste(exp_title, trial, sep='_')]
plot.event.vectors(binned.cell.df, event.var=nevents, event.thr=1) +
  geom_path(data=binned.cell.df, mapping=aes(x=x,y=100-y,group=trial_id), alpha=0.6) +
  geom_rewards(prev.locations.df, animal_name, day, 100) +
  facet_wrap(. ~ trial_name, ncol = 5) +
  theme(legend.position = 'none')


ggsave(file.path(gen_imgs_dir, paste0(cell_name, '_trial_events.svg')),
       width=23, height=8, units='cm')

plot.trace.events(binned.cell.df, event.var=nevents, event.thr=1) +
  geom_rewards(prev.locations.df, animal_name, day, 100) +
  facet_grid(. ~ exp_title)

ggsave(file.path(gen_imgs_dir, paste0(cell_name, '_exp_events.svg')),
       width=11, height=4, units='cm')
```
## Plots for the same day on selected cells
Plot traces
```{r}
#selected.cell_ids = unique(data.traces$cell_id)[1:6]
selected.cell_ids = c(83, 144, 153, 165, 
                      86, 89)
cells.traces = data.traces[trial==1 & cell_id %in% selected.cell_ids,]
cells.events = cells.traces[(is.event),]

cells.traces %>%
  ggplot(aes(x=timestamp/1000)) +
  geom_line(aes(y=trace)) +
  geom_point(data=cells.events, mapping=aes(x=timestamp/1000, y=pmax(trace) + 20), color='red', size=0.7) +
  facet_grid(cell_id ~ ., scales='free') +
  gtheme +
  xlab('Time (s)') + ylab('Fluorescence \n(background subtracted)')

ggsave('/tmp/traces_example.svg', width = 16, height = 8, units = 'cm')

```

Plot event vectors
```{r}
binned.cells.df = bin.time.space(data.traces[cell_id %in% selected.cell_ids,], 
                                 nbins.x = nbins,
                                 nbins.y = nbins,
                                 get.bin.thresholds.fun=get.quantiles.fun(c(0.95, 1.0)),
                                 binned.var='trace',
                                 timebin.dur.msec=200)
binned.cells.df[,is_running:=as.logical(is_running)]
g.events = plot.event.vectors(binned.cells.df, event.var=nevents, event.thr=1) +
  geom_path(data=binned.cells.df, mapping=aes(x=x,y=100-y,group=trial_id), alpha=0.2) +
  geom_rewards(rewards.df, animal_name, day, 100) +
  facet_wrap(. ~ cell_id, nrow = 1) +
  labs(colour='Running') +
  theme(legend.position = 'right')
g.events
```

Plot place fields
```{r}
all.pf.df = data.frame()
cell.infos = data.frame()
for (cell_name in selected.cell_ids) {
  pf = cell.spatial.info(binned.cells.df[is_running & cell_id == cell_name, ],
                         nbins, nbins,
                         trace.var = 'trace',
                         generate.plots=FALSE,
                         nshuffles=1000)
  pf.df = create.pf.df(pf$field, pf$occupancy, 
                       frame.rate=frame.rate)
  pf.df$cell_id = cell_name
  all.pf.df = bind_rows(all.pf.df, pf.df)
  cell.infos = bind_rows(cell.infos, pf$cell_info)
}

g.pf = plot.pf(all.pf.df, max.x=nbins, max.y=nbins) +
  geom_rewards(rewards.df, animal_name, day, nbins) +
  geom_text(data=cell.infos, 
            mapping=aes(x=8, y=nbins, 
                        label=paste0('SI=', 
                                     format(spatial.information, digits=2),
                                     ifelse(signif.si, '*', '') ))) +
    facet_wrap(. ~  cell_id, nrow=1) +
    labs(fill='')

g.pf
```

```{r}
g.pf_example = plot_grid(g.events, g.pf, nrow = 2, rel_widths = c(1, 1,1))
ggsave('/tmp/pf_example.svg', plot = g.pf_example, width = 16, height = 6, units = 'cm')
```


# Changes in PF over days
```{r}
#selected.days = c('2019-08-29', '2019-08-30', '2019-09-03', '2019-09-04', '2019-09-06','2019-09-07', '2019-09-08')
#all.days = place.cell.db$date %>% unique
#all.days = goal.cell.db$day_desc %>% unique
#selected.days = format(all.days)

trials.meta.df = data.table(trials.meta.df)
create.selected.pf.df = function(animal_name, cell_name) {
  selected.days = names(run.fields[[animal_name]])
  day_descs = map_chr(selected.days, ~ trials.meta.df[date==.x & animal == animal_name, day_desc][1])
  data.frame(animal=animal_name,
             cell_id=format(cell_name),
             day=selected.days,
             day_desc = day_descs,
             stringsAsFactors = FALSE)  
}

day.normalize.fields = function(pf.df) {
  pf.df %>%
    group_by(animal, date, day_desc, cell_id) %>%
    dplyr::mutate(value.field = value.field - min(value.field, na.rm=TRUE),
                  value.field = value.field / max(value.field, na.rm=TRUE))
}

place.cell.db = data.table(place.cell.db)

create.all.day.pf = function(selected.cells.df, 
                             fields.list=run.fields, 
                             occupancies.list=run.occupancies,
                             smooth.field=FALSE) {
  # Creates DF for place field of a cell specified in the row
  single.cell.pf = function(row, fields.list, occupancies.list) {
    animal_name = as.character(row$animal)
    cell_name = format(row$cell_id)
    day = format(row$day)
    
    field = fields.list[[animal_name]][[day]][[cell_name]]
    if (is.null(field)) {
      #print(paste('Field not found for', animal_name, day, cell_name))
      return(data.frame())
    }
    df = create.pf.df(field,
                      occupancies.list[[animal_name]][[day]][[cell_name]], 
                      smooth=smooth.field)
  
    df$animal = animal_name
    df$cell_id = cell_name
    return(df)
  }

  pf = selected.cells.df %>%
    adply(.margins=1, .fun=single.cell.pf, fields.list, occupancies.list) %>%
    dplyr::rename(date=day)

  return(pf)
}
  
rowwise.cell.desc = function(row) {
  animal_name = as.character(row$animal)
  cell_name = format(row$cell_id)
  day = format(row$day)
  place.db.row = place.cell.db[animal==animal_name & cell_id==cell_name & date==day,]
  row$desc = ''
  if (nrow(place.db.row) > 0) {
    row$desc = ifelse(place.db.row$signif.si, 'PC ', '')
  }
  row
}

plot.all.day.fields = function(animal_name, cell_id) {
  selected.cells.df = create.selected.pf.df(animal_name, cell_id)
  
  pf = create.all.day.pf(selected.cells.df) %>%
    day.normalize.fields()
  
  cell.desc.df = selected.cells.df %>%
    adply(.margins=1, .fun=rowwise.cell.desc) %>%
    dplyr::rename(date=day)
  
  plot.pf(pf, max.x=nbins, max.y=nbins) +
    facet_wrap(. ~ day_desc, ncol=3) +
    geom_text(data=cell.desc.df, mapping=aes(x=1, y=nbins - 2, label=desc), size=3, hjust=0) +
    geom_rewards(rewards.df, animal_name, nbins=nbins) 
}

plot.all.day.fields('E-BL', 50)
```
Multicell plot of all day activity for selected cells
```{r}
rewards.df = as.data.table(rewards.df)
animal_name = 'E-TR'

g.etr = bind_rows(
  create.all.day.pf(create.selected.pf.df(animal_name, 89)),
  create.all.day.pf(create.selected.pf.df(animal_name, 90)),
  create.all.day.pf(create.selected.pf.df(animal_name, 99)),
  create.all.day.pf(create.selected.pf.df(animal_name, 122)),
  create.all.day.pf(create.selected.pf.df(animal_name, 139)),
  ) %>% 
  filter(stringr::str_starts(day_desc, 'learning'), day_desc != 'learning3 day#3') %>% 
  day.normalize.fields() %>% 
  plot.pf(max.x=nbins, max.y=nbins) +
    facet_grid(cell_id ~ day_desc) +
    geom_rewards(rewards.df[day_desc != 'learning3 day#3',], animal_name, nbins=nbins) +
  theme(legend.position = 'top')
  
g.etr
ggsave('/tmp/pf_getr.svg', plot = g.etr, width = 22, height = 12, units = 'cm')
```


Multicell plot of several day activity for selected cells
```{r}
rewards.df = as.data.table(rewards.df)
place.cell.db = data.table(place.cell.db)
plot.rootdir = "/mnt/DATA/Prez/pf-animal-30bins-occupancy05s-deconv/"

for (animal_name in names(run.fields)) {
  plot.dir = file.path(plot.rootdir, animal_name)
  if (!file.exists(plot.dir)) {
    dir.create(plot.dir, recursive=TRUE)
  }
    
  chunk_size = 25
  cell_ids = place.cell.db[animal==animal_name, cell_id] %>% unique
  cell_chunks = split(sort(cell_ids), ceiling(seq_along(cell_ids)/chunk_size))
  merged.results.df = bind_rows(filter(rewards.df, animal == animal_name), 
                                filter(test.rewards.df, animal == animal_name, exp_title == 'beforetest') %>% 
                                  mutate(day_desc = paste0(day_desc, 't')))
  for (chunk_i in seq_along(cell_chunks)) {
    cell_chunk = cell_chunks[[chunk_i]]
    trials.pf = map_dfr(cell_chunk, ~ 
                          create.all.day.pf(create.selected.pf.df(animal_name, .x)))
    
    cell.desc.df = map_dfr(cell_chunk, ~ create.selected.pf.df(animal_name, .x)) %>%
      adply(.margins=1, .fun=rowwise.cell.desc) %>%
      dplyr::rename(date=day)
    
    beforetest.pf = map_dfr(cell_chunk, ~ 
                            create.all.day.pf(create.selected.pf.df(animal_name, .x),
                                              fields.list=beforetest.fields,
                                              occupancies.list=beforetest.occupancies)) %>%
      dplyr::mutate(day_desc = paste0(day_desc, 't'))
    
    merged.pf.data = bind_rows(trials.pf, beforetest.pf) %>%
      day.normalize.fields()
      
    g.chunk = ggplot() +
      geom_rect(data=beforetest.pf, xmin=0, xmax=100, ymin=0, ymax=100, fill='#bfbfbf', alpha=0.1) +
      geom_pf(merged.pf.data, max.x=nbins, max.y=nbins) + 
      facet_grid(cell_id ~ day_desc) +
      geom_text(data=cell.desc.df, mapping=aes(x=1, y=nbins - 2, label=desc), size=3, hjust=0) +
      geom_rewards(merged.results.df, animal_name, nbins=nbins) +
      theme(legend.position = 'top')
    
    filename = paste0('cells_', as.integer(min(cell_chunk)), '-', as.integer(max(cell_chunk)), '.png')
    ggsave(file.path(plot.dir, filename), plot=g.chunk, 
           width = 48, height = 60, units = 'cm')
  }
}
```

```{r}
animal_name = 'G-BR'
g.gbr = bind_rows(
  create.all.day.pf(create.selected.pf.df(animal_name, 46)),
  create.all.day.pf(create.selected.pf.df(animal_name, 47)),
  create.all.day.pf(create.selected.pf.df(animal_name, 102)),
  create.all.day.pf(create.selected.pf.df(animal_name, 107)),
  create.all.day.pf(create.selected.pf.df(animal_name, 139)),
  ) %>% 
  filter(stringr::str_starts(day_desc, 'learning'), day_desc != 'learning3 day#3') %>%
  day.normalize.fields() %>%
  plot.pf(max.x=nbins, max.y=nbins) +
    facet_grid(cell_id ~ day_desc) +
    geom_rewards(rewards.df[day_desc != 'learning3 day#3',], animal_name) +
  theme(legend.position = 'none')
  
g.gbr
ggsave('/tmp/pf_ggbr.pdf', plot = g.gbr, width = 22, height = 12, units = 'cm')
```


Save place fields for all days
```{r}
animal.cells.df = goal.cell.db %>%
  select(animal, cell_id) %>% 
  dplyr::distinct()

plot.rootdir = "/mnt/DATA/Prez/pf-shuffled-changed-18-05-2020/"
for (i in 1:nrow(animal.cells.df)) {
  row = animal.cells.df[i, ]
  animal_name = as.character(row$animal)
  cell_name = format(row$cell_id)
  g = plot.all.day.fields(animal_name, cell_name) +
    labs(title = paste(animal_name, cell_name))
  plot.dir = file.path(plot.rootdir, animal_name)
  if (!file.exists(plot.dir)) {
    dir.create(plot.dir, recursive=TRUE)
  }
  ggsave(file.path(plot.dir, paste0(row$cell_id, '.jpg')),
         g, width=10, height=12, units='cm')
}
```

## Plot event vectors
```{r}
animal_name = 'F-TL'
exp_title = 'beforetest'

animal.caimg_dirs = Filter(
  function(caimg_dir) {
    str_detect(caimg_dir, animal_name) & str_detect(caimg_dir, 'learning')
  },
  caimg_result_dirs)

paths.df = data.frame()
binned.events = data.frame()
for (caimg_dir in animal.caimg_dirs) {
  data.traces = read.data.trace(caimg_dir, filter_exp_title=exp_title)
  if (nrow(data.traces) > 0) {
    setorder(data.traces, trial_id, cell_id, timestamp)
    detect.events(data.traces, deconv.threshold=0.3, minpeakdistance=10)
    data.traces$is_running = as.logical(isRunning(data.traces, 2, 4, 500))
    binned.traces = bin.time.space(data.traces, 
                                   nbins.x = nbins,
                                   nbins.y = nbins,
                                   get.bin.thresholds.fun=get.quantiles.fun(c(0.2, 0.95, 1.0)),
                                   binned.var='deconv_trace',
                                   timebin.dur.msec=200)
    
    binned.events = bind_rows(binned.events, binned.traces[nevents >= 0.2, ])
    
    cell_name = binned.traces$cell_id[1]
    paths.df = bind_rows(paths.df, binned.traces[cell_id==cell_name, ])
  }
}
```

```{r}
binned.events = left_join(binned.events, trials.meta.df)
paths.df = left_join(paths.df, trials.meta.df)

binned.events = data.table(binned.events)
paths.df = data.table(paths.df)
plot.dir = file.path('/mnt/DATA/Prez/cheeseboard-events', animal_name, exp_title)
if (!file.exists(plot.dir)) {
  dir.create(plot.dir, recursive=TRUE)
}
for (cell_name in unique(binned.events$cell_id)) {
  cell.events.df = binned.events[cell_id==cell_name, ]
  g = plot.event.vectors(cell.events.df) +
    geom_path(data=paths.df, mapping=aes(x=x, y=100-y, group=trial_id), alpha=0.2) +
    geom_rewards(rewards.df, animal_name, nbins=100) +
    facet_wrap(day_desc ~ .)
  ggsave(file.path(plot.dir, paste0(cell_name, '.jpg')),
       g, width=16, height=13, units='cm')
}
```


# Population activity across space
```{r}
animal_name = 'G-BR'
exp_title='learning'
day = '2020-01-31'
root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2020-01'
#cell_name = 47

caimg_result_dir = file.path(root_dir, exp_title, day, 'caiman', animal_name, 'filtered/')
data.traces = read.data.trace(caimg_result_dir, filter_exp_title='trial')
setorder(data.traces, trial_id, cell_id, timestamp)
detect.events(data.traces, deconv.threshold=0.2)

```

```{r}
binned.traces = bin.time.space(data.traces, 
                               nbins.x = nbins,
                               nbins.y = nbins,
                               get.bin.thresholds.fun=get.quantiles.fun(c(0.2, 0.95, 1.0)),
                               binned.var='deconv_trace',
                               timebin.dur.msec=200)

all.pf.df = data.frame()

for (trial_no in unique(binned.traces$trial)) {
  pf = cell.spatial.info(binned.traces[trial == trial_no, ],
                         nbins, nbins,
                         trace.var = 'deconv_trace',
                         generate.plots=FALSE,
                         nshuffles=0,
                         min.occupancy = 1)
  pf.df = create.pf.df(pf$field, pf$occupancy, 
                       frame.rate=frame.rate,
                       min.occupancy.sec = 0.1)
  pf.df$trial = trial_no
  all.pf.df = bind_rows(all.pf.df, pf.df)
}
plot.pf(all.pf.df, max.x=nbins, max.y=nbins) +
  geom_rewards(rewards.df, animal_name, day, nbins) +
  facet_wrap(. ~ trial)
```

# Population activity across days for all mice
```{r}
all.pf.df = data.frame()
for (caimg_result_dir in caimg_result_dirs) {
  data.traces = read.data.trace(caimg_result_dir, filter_exp_title='trial')
  setorder(data.traces, trial_id, cell_id, timestamp)
  
  data.traces.immobile = data.traces[velocity <= 2.5, ]
  #detect.events(data.traces, deconv.threshold=0.2)
  data.traces.immobile$is.event = 0
  binned.traces = bin.time.space(data.traces.immobile, 
                                 nbins.x = nbins,
                                 nbins.y = nbins,
                                 get.bin.thresholds.fun=get.quantiles.fun(c(0.95, 1.0)),
                                 timebin.dur.msec=200)
  
  pf = cell.spatial.info(binned.traces,
                         nbins, nbins,
                         trace.var = 'deconv_trace',
                         generate.plots=FALSE,
                         nshuffles=0,
                         min.occupancy = 1)
  pf.df = create.pf.df(pf$field, pf$occupancy, 
                       frame.rate=5,
                       min.occupancy.sec = 1)
  pf.df$animal = data.traces$animal[1]
  pf.df$date = data.traces$date[1]
  all.pf.df = bind_rows(all.pf.df, pf.df)
}
```

```{r}
g = plot.pf(all.pf.df, max.x=nbins, max.y=nbins) +
  geom_rewards(rewards.df, nbins=nbins) +
  facet_wrap(date ~ animal) +
  scale_fill_gradientn(limits=c(0, 0.3), colours=jet.colours(7))

ggsave('/tmp/all_fields_immobile.png', g, width=20, height=20, units='cm')
g
```

