---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
library(pracma)
library(purrr)
library(readr)
library(tidyr)
library(stringr)
library(data.table)
library(datatrace)
library(tidyr)

source('locations.R')
source('utils.R')
source('traces_input.R')
source('plotting_params.R')
source('tracking_info.R')
source('behav_analysis.R')
#source('rew_aligned_activity.R')

perc2dist = 1.2
```

```{r}
mouse.meta.df = read.mouse.meta(rootdirs)
trials.meta.df = read.trials.meta(rootdirs)
```


```{r}
# root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2019-08/'
# animal_name = 'F-TL'
# exp_title='learning'
# #day = '2019-09-03'
# #day = '2019-09-05'
# day = '2019-09-07'

# root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2020-01/'
# animal_name = 'G-BR'
# exp_title='learning'
# day = '2020-02-10' # learning 3 day2

root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2019-07/'
animal_name = 'D-BR'
exp_title='learning'
day = '2019-07-29' # learning 2 day2

# root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2020-10/'
# animal_name = 'O-TR'
# exp_title='learning'
# day = '2020_10_17'

# root_dir = '/mnt/DATA/Prez/cheeseboard-down/down_2/2020-10/'
# animal_name = 'N-BR'
# exp_title='learning'
# day = '2020_10_23'

caimg_result_dir = find.caimg.dir(caimg_result_dirs, animal_name, day)
timebin.dur.msec = 200
binned.traces = prepare.binned.traces(caimg_result_dir, timebin.dur.msec=timebin.dur.msec)
#binned.traces = binned.traces[, zscored_deconv_trace := zscore(smoothed_deconv_trace), by=.(exp_title, cell_id)]

deconv_trace.matrix = reshape2::acast(binned.traces, exp_title + time_bin ~ cell_id, value.var='zscored_smooth_deconv_trace')
behav.traces = get.behav.traces(binned.traces)
```

```{r}
mobility.bouts = get.mobility.bouts(behav.traces, timebin.dur.msec=timebin.dur.msec,
                                    mobility.expr=is_running)
reward.arriving.bouts = mobility.bouts[rew_at_end>0,]

immobility.bouts = get.mobility.bouts(behav.traces, timebin.dur.msec=timebin.dur.msec,
                                      mobility.expr=!is_running)
    
#event.aligned.traces = binned.traces[, center.timestamps.around.events(.SD, mobility.bouts, exp_title[1]), 
#                                     by=.(exp_title, trial_id, cell_id)]

# Pop traces aligned to arrival at reward
```

Population activity
```{r}
pop.traces = binned.traces[, .(pop.events=sum(nevents, na.rm=TRUE) / .N, 
                               nactive=sum(nevents, na.rm=TRUE),
                               trace.mean=mean(smoothed_deconv_trace, na.rm=TRUE)),
                           by=c('exp_title', 'trial_id', 'trial', 
                                'timestamp', 'time_bin', 'x', 'y', 
                                'arrivedAtReward', 'velocity', 'atReward', 'atReward0', 'atReward1', 
                                'is_headdip', 'is_running')] 
pop.traces
```

Pop traces before arrival to reward
```{r}
# event.aligned.pop.traces = pop.traces[, center.timestamps.around.events(.SD, reward.arriving.bouts, exp_title[1]), 
#                                        by=.(exp_title, trial_id)][aligned_event_id >= 0,]
# event.aligned.pop.traces$event_seq_no = as.factor(
#   paste(event.aligned.pop.traces$trial_id, event.aligned.pop.traces$aligned_event_id, sep='_')) %>%
#   as.integer()
```


Draw population activity
```{r}
source('place_field_utils.R')
all.locations.df = map_dfr(rootdirs, read_locations)
rewards.df =  all.locations.df %>%
  filter(!is_test) %>%
  left_join(mouse.meta.df, by='animal') %>%
  left_join(trials.meta.df, by=c('date', 'animal', 'location_set'))

large.pop.events = filter(pop.traces, pop.events > 0.15)
pop.traces$trial = as.factor(pop.traces$trial)
ggplot(pop.traces) +
  geom_path(aes(x=x, y=100-y, group=trial), size=0.5) +
  #scale_colour_gradient2(low='blue', mid='white', high='red', midpoint = 0.05) +
  geom_point(data=large.pop.events, mapping=aes(x=x, y=100-y), color='red') +
  geom_rewards(rewards.df, binned.traces$animal[1], binned.traces$date[1], nbins = 100, 
               rew.colours = list(current_rew='black')) +
  #facet_wrap(trial ~ .) +
  theme_void()
```
# Activity vs running velocity

Calculate total pop activity
```{r}
total.deconv.activity = rowSums(deconv_trace.matrix) / nrow(deconv_trace.matrix)
behav.traces$total_activity = total.deconv.activity
behav.traces = behav.traces %>%
  dplyr::mutate(velocity = ifelse(velocity > 100, 100, velocity))
behav.traces = as.data.table(behav.traces)

wide.behav.traces = behav.traces %>%
  pivot_longer(c(x, y, is_headdip, is_running, velocity,  
                 atReward0, atReward1, 
                 dist_reward0, dist_reward1, moved_distance, total_activity),
               names_to='metric', values_to='value')
```

Activity raster, cells sorted using t-sne on correlation matix
```{r}
selected.trial = 1

g.behav = wide.behav.traces %>%
  filter(trial==selected.trial) %>%
  #filter(metric %in% c('velocity', 'total_activity', 'is_running')) %>% 
  filter(metric == 'total_activity') %>%
  filter(value < 50) %>%
  ggplot(aes(x=trial_time_bin * (timebin.dur.msec / 1000), y=value)) +
  geom_line() +
  facet_grid(metric ~ ., scales='free_y') +
  xlab('Time (s)')
```

Sort cells by the time of max trace value
```{r}
trial.traces = binned.traces[trial == selected.trial,]
beforetest.traces = binned.traces[exp_title == 'beforetest',]

rew.aligned.traces = binned.traces[exp_title=='trial' & trial == selected.trial, 
                                   center.timestamps.around.events(.SD, reward.arriving.bouts[trial == selected.trial], 
                                                                   exp_title[1],
                                                                   padding.after.event=5000/timebin.dur.msec), 
                                   by=.(exp_title, trial_id, cell_id)][aligned_event_id >= 0,]
cell.order.df = order.cells.by.max.val(rew.aligned.traces[timestamp_from_start >= 0 & timestamp_from_end <= 5000])
```

```{r}
plotted.trials = c(selected.trial)
plot.binned.traces = binned.traces[trial %in% plotted.trials,]
joined.binned.traces = plot.binned.traces[cell.order.df, on='cell_id']
g.raster = plot.activity.raster(joined.binned.traces[is.active==TRUE,], 
                                zscored_smooth_deconv_trace, 
                                tile.width=timebin.dur.msec/1000) +
  geom_vline(data=reward.arriving.bouts[trial %in% plotted.trials], 
             aes(xintercept=timestamp_end/1000), 
             linetype='dashed', color='#333333') +
  geom_vline(data=reward.arriving.bouts[trial %in% plotted.trials], 
             aes(xintercept=timestamp_start/1000), 
             linetype='dashed', color='#0098ff') +
  facet_grid(trial ~ .)
g.raster

plot_grid(g.raster + xlim(c(0, 80)), 
          g.behav + xlim(c(0, 80)), 
          ncol=1, 
          #rel_heights = c(5, 1.4))
          rel_heights = c(3,2))

ggsave('~/tmp/cheeseboard/pop_activity/dca1_sequence.pdf', 
       height=7, width=10, units='cm', device=cairo_pdf, dpi=300)

behav.traces.fragment = behav.traces[trial==selected.trial & timestamp>=53000 & is_running]
behav.traces.fragment$row_id = 1:nrow(behav.traces.fragment)
ggplot(behav.traces.fragment) +
  geom_path(aes(x=as.integer(x), y=as.integer(100-y), color=row_id)) +
  xlim(c(0,100)) +
  ylim(c(0,100)) +
  geom_rewards.current(rewards.df, subject = animal_name, day = day, nbins=100, rew.size=4, stroke.size=1) +
  geom_maze_contour(100) +
  scale_color_continuous(low='#b8e2ff', high='#222222') +
  gtheme +
  theme_void() +
  labs(color='Time (s)') +
  theme(legend.position='bottom') 
ggsave('~/tmp/cheeseboard/pop_activity/dca1_running_path.pdf', 
       height=6.3, width=5, units='cm', device=cairo_pdf, dpi=300)

```

```{r}
df = binned.traces[trial == selected.trial & timestamp > 0 * 1000, ]
cell.order.df = order.cells.by.max.val(df, active.val.threshold = 0.1)
df.joined = df[cell.order.df, on = .(cell_id)]
plot.activity.raster(df.joined, zscored_trace, tile.width=timebin.dur.msec/1000) +
  xlim(c(0,35))
ggsave('~/tmp/cheeseboard/pop_activity/dca1_sequence2.png', 
       height = 7, width = 7, units = 'cm')
```
Reward centered
```{r}
timebin.dur.msec = 200
selected.trial=6
rew.aligned.traces = binned.traces[exp_title=='trial' & trial == selected.trial, 
                                   center.timestamps.around.events(.SD, reward.arriving.bouts[trial == selected.trial], 
                                                                   exp_title[1],
                                                                   padding.after.event=5000/timebin.dur.msec), 
                                   by=.(exp_title, trial_id, cell_id)][aligned_event_id >= 0,]
rew.aligned.traces.fragment = rew.aligned.traces[timestamp_from_start >= 0 & timestamp_from_end <= 5000 & timestamp_from_end >= -6000]
gs = plot.approaches(rew.aligned.traces.fragment,
                     rew.aligned.traces.fragment$trial_id[1], 
                     return.plots = TRUE, 
                     cell.active.thr = 0.1, 
                     include.summary.plots = FALSE)

event.ids = unique(rew.aligned.traces.fragment$aligned_event_id)
event.index = 1
behav.fragment.event = rew.aligned.traces.fragment[aligned_event_id==event.ids[event.index] & timestamp_from_end <= 0 &
                                                   cell_id==rew.aligned.traces.fragment$cell_id[1]]

g.approach.path = ggplot(behav.fragment.event) +
  geom_path(aes(x=as.integer(x), y=as.integer(100-y), color=timestamp_from_end/1000)) +
  xlim(c(0,100)) +
  ylim(c(0,100)) +
  geom_rewards.current(rewards.df, subject = animal_name, day = day, nbins=100, rew.size=4, stroke.size=1) +
  geom_maze_contour(100) +
  scale_color_continuous(low='#b8e2ff', high='#222222') +
  theme_void() +
  labs(color='Time (s)') +
  theme(legend.position='bottom')
g.approach.path

ggsave(paste0(behav.fragment.event$trial_id[1], '_approach_', event.index, '.pdf'), 
       g.approach.path,
       path = '/home/prez/tmp/cheeseboard/approaches_selected',
       width=5, height=6.3, units='cm', device=cairo_pdf, dpi=300)

gs[[event.index]]
ggsave(paste0(behav.fragment.event$trial_id[1], '_activity_', event.index, '.pdf'), 
       gs[[event.index]],
       path = '/home/prez/tmp/cheeseboard/approaches_selected',
       width=3.5, height=3.35, units='cm', device=cairo_pdf, dpi=300)
```

```{r}
beforetest.reward.approaches = get.reward.approaches(behav.traces[exp_title == 'beforetest'], 
                                                     timebin.dur.msec=timebin.dur.msec, 3000)[rew_dist_at_end < 15]
day.beforetest.aligned.pop.traces = get.event.aligned.pop.traces(binned.traces[exp_title == 'beforetest'], 
                                                                 beforetest.reward.approaches)
beforetest.aligned.traces = binned.traces[, center.timestamps.around.events(.SD, beforetest.reward.approaches, exp_title[1],
                                                                            padding.after.event=2000/timebin.dur.msec), 
                                          by=.(exp_title, trial_id, cell_id)][aligned_event_id >= 0,]
```

```{r}
g.approaches = list()
for (event_id in beforetest.reward.approaches$event_id) {
  approach.traces = beforetest.aligned.traces[aligned_event_id==event_id & timestamp_from_start >=0 & timestamp_from_end <= 2000,]
  behav.approach.trace = approach.traces[cell_id == approach.traces$cell_id[1],]
  cell.order.df = order.cells.by.max.val(approach.traces, active.val.threshold=0.5)
  df.joined = approach.traces[cell.order.df, on=.(cell_id)]
  g.activity = plot.activity.raster(df.joined, fill.var=zscored_smooth_deconv_trace, xvar=timestamp_from_end, tile.width=timebin.dur.msec/1000)
  g.behav = ggplot(behav.approach.trace) +
    #geom_line(aes(x=timestamp_from_end/1000, y=smooth_velocity)) +
    geom_line(aes(x=timestamp_from_end/1000, y=pmin(dist_reward0, dist_reward1))) +
    xlab('Time (s)') + ylab('Velocity') + gtheme
  g.approaches[[event_id]] = cowplot::plot_grid(g.activity, g.behav, ncol=1, rel_heights = c(2,1))
}

napproaches = length(g.approaches)
nrows = ceil(napproaches/3)
ggsave('beforetest_approaches.png',
      plot = cowplot::plot_grid(plotlist=g.approaches, ncol = 3), 
      path = '/tmp',
      height=nrows*7, width=15, units='cm')
```


```{r}
goal.cell.max.dist = 20
in.reward.zone.sec = df.joined[dist_reward1 < goal.cell.max.dist * perc2dist, 
                               unique(trial_time_bin * (timebin.dur.msec / 1000))]

library(MASS)
regressed.df = df.joined %>%
  filter(is.active) %>%
  filter(nevents > 0) %>%
  dplyr::mutate(trial.time.sec = trial_time_bin * (timebin.dur.msec / 1000))   %>%
  filter(trial.time.sec < 15) 

seq.model.before = MASS::ltsreg(cell_order ~ trial.time.sec, data=regressed.df, subset = trial.time.sec < in.reward.zone.sec)
summary(seq.model.before)
#seq.model.before$coefficients
seq.model.rew = MASS::ltsreg(cell_order ~ trial.time.sec, data=regressed.df, subset = trial.time.sec >= in.reward.zone.sec[1] & trial.time.sec < 53)
summary(seq.model.rew)

ggplot(regressed.df, aes(x=trial.time.sec, y=cell_order)) +
  geom_point() +
  geom_abline(intercept=-seq.model.before$coefficients[1], slope = -seq.model.before$coefficients[2]) +
  geom_abline(intercept=-seq.model.rew$coefficients[1], slope = -seq.model.rew$coefficients[2]) +
  scale_y_reverse() +  
  geom_vline(xintercept = min(in.reward.zone.sec), linetype='dashed') +
  gtheme

```

## Firing in a a sequence vs other places
```{r}
rew.aligned.traces = binned.traces[, center.timestamps.around.events(.SD, reward.arriving.bouts, exp_title[1]), 
                                    by=.(exp_title, trial_id, cell_id)][aligned_event_id >= 0,]

# TimeBin with 600 msec window
seq.max.sec = 10
window.dur.msec = 1000
rew.aligned.traces = rew.aligned.traces[timestamp_from_end <= 0.0 & timestamp_from_end >= -seq.max.sec * 1000.0,
  `:=` (roll.nevents = zoo::rollmean(as.double(nevents), 
                                     round(window.dur.msec / timebin.dur.msec / 2), 
                                     fill=c(0,0,0), align='center')),
  by=.(animal, date, exp_title, trial_id, trial, cell_id, aligned_event_id)][
    , timestamp_to_max := timestamp_from_start - timestamp_from_start[which.max(roll.nevents)],
    by=.(animal, date, exp_title, trial_id, trial, cell_id, aligned_event_id)]

rew.aligned.traces[timestamp_from_end <= 0.0 & timestamp_from_end >= -seq.max.sec * 1000.0, 
                   .(nevents_inside = as.integer(sum(ifelse(abs(timestamp_to_max) <= window.dur.msec / 2, nevents, 0))),
                     nevents = sum(nevents),
                     bout_dur = max(timestamp) - min(timestamp)),
                   by=.(exp_title, trial_id, cell_id, aligned_event_id)] ->
  cell.fr.outside.seq
```


## Plot by distance run
```{r}
cell.order.df = order.cells.by.max.val(trial.traces[timestamp > 35 * 1000, ])
max.moved.dist = ceiling(max(binned.traces$moved_distance))
dist.nbins = 100
dist.traces = stimbin.traces(binned.traces[trial == selected.trial & timestamp > 35 * 1000, ], 
                             moved_distance, dist.nbins, max.width = max.moved.dist)
binned.dist.traces = dist.traces[, .(mean.norm_deconv_trace = max(zscored_deconv_trace),
                                     #mean.norm_trace = max(norm_trace),
                                     atReward=mean(atReward0 + atReward1)), 
                                 by=.(animal, date, trial, cell_id, bin.moved_distance)]
binned.dist.traces$atReward = as.factor(ifelse(binned.dist.traces$atReward > 0.5, 'at_reward', 'not_at_reward'))

g.raster = binned.dist.traces[bin.moved_distance > 0] %>%
  #filter(trial %in% c(6,7,8)) %>%
  filter(!is.na(bin.moved_distance) ) %>%
  left_join(cell.order.df, by='cell_id') %>% 
  ggplot() +
  geom_tile(aes(x=round(bin.moved_distance * max.moved.dist / dist.nbins), 
                  y=as.integer(cell_order), 
                  fill=mean.norm_deconv_trace,
                  width=5, height=1)) +
  geom_tile(aes(x=round(bin.moved_distance  * max.moved.dist / dist.nbins), y=-2, color=atReward)) +
  xlab('Distance run (cm)') +
  ylab('Cell') +
  gtheme +
  theme(legend.position = 'none') +
  facet_grid(trial ~ .) +
  scale_fill_gradient(low='white', high = 'black') +
  scale_color_manual(values=c('#0098ffff', 'white')) +
  scale_y_reverse()

dist.behav.traces = behav.traces %>%
  dplyr::mutate(trial_time_sec = trial_time_bin * (timebin.dur.msec / 1000)) %>%
  pivot_longer(c(x, y, is_headdip, is_running, trial_time_sec, velocity, atReward0, atReward1,  
                 dist_reward0, dist_reward1, angle),
               names_to='metric', values_to='value')
g.dist.behav = dist.behav.traces %>%
  filter(trial==selected.trial) %>%
  #filter(metric %in% c( 'trial_time_sec', 'velocity')) %>%
  filter(metric == 'velocity', value < 50) %>% 
  ggplot(aes(x=moved_distance, y=value)) +
  geom_line() +
  facet_grid(metric ~ ., scales='free_y') +
  xlab('Distance (cm)')
plot_grid(g.raster, g.dist.behav, ncol=1, rel_heights = c(3, 1))

```

Find periods of approach to reward
```{r}
data.traces = as.data.table(data.traces)
data.traces.approach = group_by(data.traces[exp_title == 'trial',], animal, exp_title, trial, cell) %>%
  arrange(trial, cell, timestamp) %>%
  dplyr::mutate(
    rew0.approach.timestamp = reward.approach.timestamp(atReward0, timestamp),
    rew1.approach.timestamp = reward.approach.timestamp(atReward1, timestamp),
    rew0.approach = is.reward.approach(atReward0,
                                       atReward1,
                                       timestamp),
    rew1.approach = is.reward.approach(atReward1,
                                       atReward0,
                                       timestamp)) %>%
  as.data.table()

data.traces.approach %>%
  filter(rew0.approach, cell_id == 0) %>% 
  filter(velocity < 50) %>% 
  ggplot() +
  geom_tile(aes(x=round(-dist_reward0 * perc2dist), y=trial, fill=velocity, width=3)) +
  #geom_tile(aes(x=round(rew1.approach.timestamp), y=trial, fill=velocity, width=100)) +
  scale_fill_gradient(low='grey80', high = 'black') +
  xlab('Distance to reward (cm)') +
  gtheme

data.traces.approach %>%
  filter(rew0.approach, cell_id == 0) %>% 
  filter(velocity < 50) %>% 
  ggplot() +
  geom_tile(aes(x=round(rew0.approach.timestamp), y=trial, fill=velocity, width=100)) +
  scale_fill_gradient(low='grey80', high = 'black') +
  xlab('Time to reward (s)') +
  gtheme


rew0.approach.df = filter(data.traces.approach, rew0.approach) %>%
  filter(velocity < 50) %>%
  dplyr::select(exp_title, trial, timestamp, cell_id, dist_reward0, velocity, deconv_trace) %>%
  dplyr::distinct()

cor(rew0.approach.df$velocity, rew0.approach.df$dist_reward0)

# The cells active at reward are activity anticorrelated with velocitymore than other cells
group_by(rew0.approach.df, exp_title, cell_id) %>%
  dplyr::summarise(cor.df2velocity = cor(velocity, deconv_trace),
                   rew0.weighted.dist = weighted.mean(dist_reward0, deconv_trace)) %>% 
  ggplot() +
  geom_point(aes(x=cor.df2velocity, y=rew0.weighted.dist)) +
  gtheme
```

```{r}
behav.traces %>%
  #filter(trial == 1) %>%
  dplyr::mutate(velocity = velocity / 20000) %>%
  dplyr::mutate(atReward = (atReward0 + atReward1) / 2000) %>%
  dplyr::select(trial, timestamp, velocity, total_activity, atReward) %>%
  tidyr::pivot_longer(c(velocity, total_activity, atReward), names_to='metric', values_to='value') %>%
  ggplot(aes(x=timestamp/1000, metric)) +
  geom_line(aes(y=value)) +
  facet_grid(trial + metric ~ ., space = 'free_y', scales='free_y') +
  #xlim(c(5,200)) +
  gtheme
```
## Principal components of activity plotted vs behavioural variables
```{r}
pca.res = prcomp(deconv_trace.matrix, center = TRUE, scale. = TRUE)
cumvar = cumsum(pca.res$sdev*pca.res$sdev)
cumvar.portion = cumvar / cumvar[length(cumvar)]
npc = which(cumvar.portion >= 0.9) %>% first
response.df = as.data.frame(pca.res$x[,1:npc])
response.df$time_bin = as.integer(rownames(deconv_trace.matrix))
response.df = as.data.table(response.df)
joined.response.df = response.df[behav.traces, on='time_bin']
melt.pc.df = data.table::melt(joined.response.df, id.vars=c('time_bin', 'trial_time_bin', 'trial'))

```

Plot pcs over time
```{r}
melt.pc.df %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'velocity', 'total_activity')) %>%
  filter(trial < 3) %>%
  #filter(variable %in% c('PC1')) %>%
  ggplot() +
  geom_line(aes(x=trial_time_bin, y=value)) +
  facet_grid(trial + variable ~ ., scales='free_y')
```

```{r}
m = lm(log(total_activity) ~ velocity + atReward0 + atReward1 + angle + dist_reward0 + dist_reward1, 
       data=joined.response.df)
       #subset = atReward0 + atReward1 < 0.1)
summary(m)
```
# Cell correlations

For all day
```{r}
source('correlations.R')
C = cor(deconv_trace.matrix)
image(C)
shuffled.cors.df = get.shuffled.cors.df(deconv_trace.matrix, 100)
cors.df = create.cor.values.df(C)
#cors.pvals = test.cors.not.different(shuffled.cors.df, cors.df)
#pval=quantile(cors.pvals, c(0.95))[1]
plot.shuffled.cors(shuffled.cors.df, cors.df)
```

For running epochs vs immobility
```{r}
running.trace.matrix = reshape2::acast(binned.traces[is_running > 0], time_bin ~ cell_id, value.var='norm_deconv_trace')
immobility.trace.matrix = reshape2::acast(binned.traces[is_running == 0], time_bin ~ cell_id, value.var='norm_deconv_trace')
plot.shuffled.cors(create.cor.values.df(cor(immobility.trace.matrix)),
                   create.cor.values.df(cor(running.trace.matrix)), 
                   shuffled.label = 'immobility', original.label='running') +
  gtheme
```
# Cell traces Cross-Correlations
Cross-correlations on a sequence ordered by the max trace value.
This doesn't make sense - after found a sequence, need to keep lags within the sequence.
```{r}
running.trial.trace.matrix = reshape2::acast(binned.traces[is_running > 0 & trial == 1,], 
                                             time_bin ~ cell_id, value.var='norm_deconv_trace')

ncells = ncol(running.trial.trace.matrix)
cell_index_pairs = combn(seq_len(ncells),2)

cell.max.time.i = apply(running.trial.trace.matrix, 2, which.max)
cell.order.df = data.frame(cell_id=cell_ids, 
                           max.time.i=cell.max.time.i) %>%                
  dplyr::arrange(cell.max.time.i) %>%                                                       
  dplyr::mutate(cell_order = dplyr::row_number())

ccov.df = data.frame()
ncells.compared = 1

for (trial_i in unique(binned.traces$trial)) {
  trial.trace.matrix = reshape2::acast(binned.traces[is_running > 0 & trial == trial_i,], 
                                       time_bin ~ cell_id, value.var='norm_deconv_trace')
  for (i in 1:(ncells - 1)) {
    for (j in (i+1):min(ncells, i+ncells.compared)) {
      fst.cell.i = cell.order.df$cell_id[i]
      snd.cell.i = cell.order.df$cell_id[j]
      
      CC = ccf(trial.trace.matrix[,fst.cell.i], 
               trial.trace.matrix[,snd.cell.i], 
               lag.max = 10 * (1000 / timebin.dur.msec),
               type = 'correlation', 
               plot=FALSE)
      
      #max.lag.index = (length(CC$lag) - 1) / 2 + which.max(CC$acf[((length(CC$lag) - 1) / 2) : length(CC$lag)])
      max.lag.index = which.max(CC$acf)
      ccov.df = bind_rows(
        ccov.df, 
        list(fst.cell = colnames(trial.trace.matrix)[fst.cell.i],
             snd.cell = colnames(trial.trace.matrix)[snd.cell.i],
             trial = trial_i,
             lag.sec = CC$lag[max.lag.index] * timebin.dur.msec / 1000,
             ccor = CC$acf[max.lag.index],
             ccor0 = CC$acf[(length(CC$lag) + 1) / 2]))
    }
  }
}

```

```{r}
ccov.df$trial = as.factor(ccov.df$trial)
ggplot(ccov.df, aes(x=lag.sec, y=ccor)) + 
  geom_point(shape=1) +
  geom_smooth() +
  facet_wrap(trial ~ .) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  gtheme
```

Correlated cells stay correlated acros trials - but that does not prove about the stable sequence
```{r}
ccov.df = dplyr::mutate(ccov.df, cell_pair = paste(fst.cell, snd.cell, sep='x'))
high.cor.trial1.pairs = subset(ccov.df, trial == 1 & ccor0 > 0.4)$cell_pair
ggplot(ccov.df, aes(x=trial, y=ccor0, color=cell_pair %in% high.cor.trial1.pairs)) + 
  geom_violin()
```

# Cross Correlation between velocity and pop activity


Activity preceedes higher velocity by 5 sec for G-BR learning1 day 1
Simultaneous for G-BR learning1 day4 and day5

K-BR - signal preceeding velocity - 
Signal preceeding velocity:
- slowing down at reward when highest activity
- starting to move after a pop event

TODO: left-skewed lag distribution...
look at rew preceeding and rew proceeding epochs separetely
```{r}
population.cors = tibble(trial=integer(), 
                         peak.lag.ms=integer(),
                         peak.cor=numeric(),
                         cor.signif.level=numeric())
for (trial_i in unique(behav.traces$trial)) {
  trial_subset = which(behav.traces$trial == trial_i)
  trace.velocity.ccf = ccf(total.deconv.activity[trial_subset], 
                           behav.traces$velocity[trial_subset], 
                           lag.max=20 * 1000/timebin.dur.msec, 
                           type='correlation', 
                           plot=FALSE)
  signif.level = qnorm((1 + 0.95)/2)/sqrt(trace.velocity.ccf$n.used)
  
  max.acf.i = which.max(trace.velocity.ccf$acf)
  peak.lag.ms = trace.velocity.ccf$lag[max.acf.i] * (timebin.dur.msec)
  
  population.cors = tibble::add_row(population.cors, trial=trial_i, 
                                                  peak.lag.ms=peak.lag.ms,
                                                  peak.cor=trace.velocity.ccf$acf[max.acf.i],
                                                  cor.signif.level=signif.level)
}
```

# Analysis on ccor for all data

Percent of trials with signif corrs
```{r}
all.population.cors %>%
  left_join(trials.meta.df) %>%
  left_join(mouse.meta.df) %>%
  group_by(exp_title, implant) %>%
  dplyr::summarise(cors.signif = mean(peak.cor > cor.signif.level))
```

```{r}
all.population.cors %>%
  filter(peak.cor > cor.signif.level) %>%
  left_join(trials.meta.df) %>%
  left_join(mouse.meta.df) %>%
  group_by(implant, day_desc, exp_title, animal) %>%
  #dplyr::summarise(peak.lag.ms.med=median(peak.lag.ms), peak.cor.med=median(peak.cor)) %>%
  filter(day_desc %in% c('habituation day#3', 'learning1 day#3', 'learning1 day#4', 'learning1 day#5', 'learning2 day#1', 'learning2 day#2')) %>%
  ggplot() +
  geom_point(aes(x=peak.lag.ms, y=peak.cor, color=animal)) +
  facet_grid(animal + implant ~ day_desc) +
  geom_vline(xintercept = 0, linetype='dashed') +
  gtheme +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



Principal components analysis
```{r}
day.pca = prcomp(response.matrix, center = TRUE, scale. = TRUE)

day.pca$x[,1:50] %>% image
```

#NMF
```{r}
library(NMF)

res20 <- nmf(t(response.matrix), 20, seed='nndsvd')
t(coef(res20))[,1:20] %>% image
```

Population activity at reward:

```{r}
source('tracking_info.R')

get_index_arrived = function(at.reward.vec, timestamps) {
  indecies = which(at.reward.vec == 1)
  if (length(indecies) == 0) {
    return(-1)
  }
  return(timestamps[indecies[1]])
}

aligned.data.df = filter(data.traces) %>%
         group_by(trial_id, date, trial, cell) %>%
         # mutate(at_rew0 = is.at.reward(velocity, dist_reward0, timestamp, running.thresh = 2),
         #        at_rew1 = is.at.reward(velocity, dist_reward1, timestamp, running.thresh = 2)) %>%
         mutate(arrived.rew0=get_index_arrived(atReward0, timestamp),
                arrived.rew1=get_index_arrived(atReward1, timestamp),
                timestamp.rew0 = timestamp  - arrived.rew0,
                timestamp.rew1 = timestamp - arrived.rew1) %>%
         ungroup()
```



```{r}
is.within = function(val, range=c(-3000, 20000)) {
  return (val >= range[1] & val <= range[2])
}

trace.at.reward = dplyr::filter(aligned.data.df, is.within(timestamp.rew1)) %>%
  dplyr::rename(timestamp.rew = timestamp.rew1)
```

```{r}
time_bin_sec = 1
pop.mean.at.reward = trace.at.reward %>%
  mutate(timestamp_bin = floor(timestamp.rew / time_bin_sec / 1000)) %>%
  group_by(trial, timestamp_bin) %>%
  dplyr::summarise(trace.mean = mean(trace))
```

```{r}
ggplot(pop.mean.at.reward) +
  geom_raster(aes(x=timestamp_bin, y=trial, fill=trace.mean))
```

